---
title: "DISH intake24 processing"
output: word_document
---

This notebook processes intake24 data to derive day and participant level values. 

# Prepare R Environment
```{r message=FALSE, warning=FALSE, include=FALSE}

#clear R environment
rm(list = ls())

#load required packages
library(dplyr)
library(tidyr)
library(rio)
library(ggplot2)
library(ggthemes)
library(grafify)
library(lubridate)
library(stringr)
library(readxl)
library(flextable)
library(gtsummary)
library(writexl)
library(forcats)
library(openxlsx)
```

# Import the data
```{r include=FALSE}
df.intake24_item <- read.csv( "/Users/ricki/Desktop/DISH_data_cleaning/Output/intake24_item_050924.csv") 
df.survey <- read.csv( "/Users/ricki/Desktop/DISH_data_cleaning/Output/survey_clean_050924.csv") 

#df.intake24_item <- read.csv( "C:/Users/ljaacks/OneDrive - University of Edinburgh/Scottish Diets/_National Monitoring of Diet Scotland/3_DISH/Analysis/Data/intake24_item_280824.csv")
#df.survey <- read.csv( "C:/Users/ljaacks/OneDrive - University of Edinburgh/Scottish Diets/_National Monitoring of Diet Scotland/3_DISH/Analysis/Data/survey_clean_280824.csv")
```

# Recall Level Values
## Total daily nutrient and food group intake (across items)
```{r echo=FALSE, message=FALSE, warning=FALSE}
  df.intake24_recall <- df.intake24_item %>% 
      group_by(UserID, RecallNo) %>%
      summarise(
        HouseholdID = first(HouseholdID),
        psu = first(psu),
        Device_group = first(Device_group),
        Age = first(Age),
        age_cat = first(age_cat),
        Sex = first(Sex),
        age_sex_cat = first(age_sex_cat),
        age_cat_drv = first(age_cat_drv),
        age_sex_cat_drv = first(age_sex_cat_drv),
        Ethnicity = first(Ethnicity),
        simd_quintile = first(simd_quintile),
        Education = first(Education),
        adults_cat = first(adults_cat),
        children_cat = first(children_cat),
        FoodParcels = first(FoodParcels),
        NumberOfRecalls = first(NumberOfRecalls), 
        Day_Energykcal = sum(Energykcal),
        Day_FoodEnergy = sum(FoodEnergy),
        Day_FoodMilkEnergy = sum(FoodMilkEnergy),
        Day_TotalGrams = sum(TotalGrams),
        Day_FoodGrams = sum(FoodGrams),
        Day_FoodMilkGrams = sum(FoodMilkGrams),
        Day_Carbohydrateg = sum(Carbohydrateg),
        Day_Carbs_kcal=sum(Carbs_kcal),
        Day_FreeSugarsg = sum(Freesugarsg), 
        Day_FreeSugars_kcal=sum(Freesugars_kcal),
        Day_Fatg = sum(Fatg),
        Day_Fat_kcal=sum(Fat_kcal),
        Day_SatFatg = sum(Saturatedfattyacidsg),
        Day_SatFat_kcal=sum(SatFat_Kcal),
        Day_TransFatg = sum(Transfattyacidsg),
        Day_TransFat_kcal=sum(TransFat_Kcal),
        Day_Proteing = sum(Proteing),
        Day_Protein_kcal = sum(Protein_kcal),
        Day_Alcoholg = sum(Alcoholg),
        Day_Alcohol_kcal = sum(Alcohol_kcal),
        Day_AOACFibreg = sum(AOACg),
        Day_VitaminAug = sum(VitaminAug),
        Day_Riboflavinmg = sum(Riboflavinmg),
        Day_Folateug = sum(Folateug),
        Day_VitaminDug = sum(VitaminDug),
        Day_VitaminB12ug = sum(VitaminB12ug),
        Day_VitaminCmg = sum(VitaminCmg),
        Day_Ironmg = sum(Ironmg),
        Day_Calciummg = sum(Calciummg),
        Day_Sodiummg = sum(Sodiummg),
        Day_Saltg = sum(Saltg), 
        Day_Magnesiummg = sum(Magnesiummg),
        Day_Potassiummg = sum(Potassiummg),
        Day_Iodineug = sum(Iodineug),
        Day_Seleniumug = sum(Seleniumug),
        Day_Zincmg = sum(Zincmg),
        
        Day_redmeatg = sum(TotalGrams[ReportingFoodGroupCode == 1 ], na.rm = TRUE),
        Day_processedmeatg = sum(TotalGrams[ReportingFoodGroupCode == 2], na.rm = TRUE),
        Day_redprocessedmeatg = sum(TotalGrams[ReportingFoodGroupCode %in% c(1, 2)], na.rm = TRUE),
        Day_oilyfishg = sum(TotalGrams[ReportingFoodGroupCode == 3], na.rm = TRUE),
        Day_fruitg = sum(TotalGrams[ReportingFoodGroupCode == 4], na.rm = TRUE),
        Day_vegg = sum(TotalGrams[ReportingFoodGroupCode == 5], na.rm = TRUE),
        Day_fruitvegg = sum(TotalGrams[ReportingFoodGroupCode %in% c(4, 5)], na.rm = TRUE),
        Day_fruitjuiceg = sum(TotalGrams[ReportingFoodGroupCode == 6], na.rm = TRUE),
        Day_ssbg = sum(TotalGrams[ReportingFoodGroupCode == 7], na.rm = TRUE),
        Day_sugarconfecg = sum(TotalGrams[ReportingFoodGroupCode == 8], na.rm = TRUE),
        Day_chocolateconfecg = sum(TotalGrams[ReportingFoodGroupCode == 9], na.rm = TRUE),
        Day_sweetbiscuitsg = sum(TotalGrams[ReportingFoodGroupCode == 10], na.rm = TRUE),
        Day_savourybiscuitsg = sum(TotalGrams[ReportingFoodGroupCode == 11], na.rm = TRUE),
        Day_cakespiesg = sum(TotalGrams[ReportingFoodGroupCode == 12], na.rm = TRUE),
        Day_savourysnacksg = sum(TotalGrams[ReportingFoodGroupCode == 13], na.rm = TRUE),
        Day_pizzasg = sum(TotalGrams[ReportingFoodGroupCode == 14], na.rm = TRUE),
        Day_readymealsg = sum(TotalGrams[ReportingFoodGroupCode == 15], na.rm = TRUE),
        Day_icecreamg = sum(TotalGrams[ReportingFoodGroupCode == 16], na.rm = TRUE),
        Day_cerealsg = sum(TotalGrams[ReportingFoodGroupCode == 17], na.rm = TRUE),
        Day_chipsg = sum(TotalGrams[ReportingFoodGroupCode == 18], na.rm = TRUE),
        Day_yoghurtdairydessertg = sum(TotalGrams[ReportingFoodGroupCode == 19], na.rm = TRUE),
        
        Day_RRPMg = sum(Beefg, Lambg, Porkg, ProcessedRedMeatg, OtherRedMeatg, Burgersg, Sausagesg, Offalg),
        Day_FV_Beansg = sum(Beansg),
        Day_FV_FruitJuiceg = sum(FruitJuiceg),
        Day_FV_Smoothieg = sum(SmoothieFruitg),
        Day_FV_DriedFruitg = sum(DriedFruitg),
        Day_FV_FreshFruitg = sum(Fruitg),
        Day_FV_Vegg = sum(Tomatoesg, TomatoPureeg, Brassicaceaeg, YellowRedGreeng, OtherVegg)) %>%
    ungroup()
  
  df.intake24_recall <- df.intake24_recall %>%
    mutate(Day_FV_JuiceSmoothieg = Day_FV_FruitJuiceg + Day_FV_Smoothieg)
  
  df.intake24_recall <- df.intake24_recall %>%
    mutate(Day_FV_Portions_Beans = case_when(
            Age >= 2 & Age < 11 & Day_FV_Beansg > 40 ~ 1,
            Age >= 2 & Age < 11 & Day_FV_Beansg <= 40 ~ Day_FV_Beansg/40,
            Age >= 11 & Age < 16 & Day_FV_Beansg > 80 ~ 1,
            Age >= 11 & Age < 16 & Day_FV_Beansg <= 80 ~ Day_FV_Beansg/80,
            TRUE ~ NA),
          
          Day_FV_Portions_JuiceSmoothie = case_when(
            Day_FV_JuiceSmoothieg >150 ~ 1,
            Day_FV_JuiceSmoothieg <= 150 ~ Day_FV_JuiceSmoothieg/150,
            TRUE ~ NA),
          
          Day_FV_Portions_DriedFruit = case_when(
            Age >= 2 & Age < 11 ~ Day_FV_DriedFruitg/15,
            Age >= 11 & Age < 16 ~ Day_FV_DriedFruitg/30,
            TRUE ~ NA),
          
          Day_FV_Portions_FreshFruit = case_when(
            Age >= 2 & Age < 11 ~ Day_FV_FreshFruitg/40,
            Age >= 11 & Age < 16 ~ Day_FV_FreshFruitg/80,
            TRUE ~ NA),
          
          Day_FV_Portions_Veg = case_when(
            Age >= 2 & Age < 11 ~ Day_FV_Vegg/40,
            Age >= 11 & Age < 16 ~ Day_FV_Vegg/80,
            TRUE ~ NA))
  
  df.intake24_recall <- df.intake24_recall %>%
    mutate(Day_FV_Portions_Total = Day_FV_Portions_Beans+Day_FV_Portions_JuiceSmoothie+Day_FV_Portions_DriedFruit+Day_FV_Portions_FreshFruit+Day_FV_Portions_Veg,
           Day_FV_Portions_Total_NoJuiceSmoothie = Day_FV_Portions_Beans+Day_FV_Portions_DriedFruit+Day_FV_Portions_FreshFruit+Day_FV_Portions_Veg) %>%
    relocate(Day_FV_Beansg, Day_FV_Portions_Beans, Day_FV_FruitJuiceg, Day_FV_Smoothieg, Day_FV_JuiceSmoothieg, Day_FV_Portions_JuiceSmoothie, Day_FV_DriedFruitg, 
             Day_FV_Portions_DriedFruit, Day_FV_FreshFruitg, Day_FV_Portions_FreshFruit, Day_FV_Vegg, Day_FV_Portions_Veg, Day_FV_Portions_Total, Day_FV_Portions_Total_NoJuiceSmoothie, .after = Day_icecreamg)
```

## Intakes as a percentage of energy
```{r}
df.intake24_recall <- df.intake24_recall %>%
      mutate(
        Day_Carbs_PropFoodEnergy = (Day_Carbs_kcal/Day_FoodEnergy)*100,
        Day_FreeSugars_PropFoodEnergy = (Day_FreeSugars_kcal/Day_FoodEnergy)*100,
        Day_Fat_PropFoodEnergy = (Day_Fat_kcal/Day_FoodEnergy)*100,
        Day_SatFat_PropFoodEnergy = (Day_SatFat_kcal/Day_FoodEnergy)*100,
        Day_TransFat_PropFoodEnergy = (Day_TransFat_kcal/Day_FoodEnergy)*100,
        Day_Protein_PropFoodEnergy = (Day_Protein_kcal/Day_FoodEnergy)*100) %>%
      relocate(Day_Carbs_PropFoodEnergy, .after = Day_Carbs_kcal) %>%
      relocate(Day_FreeSugars_PropFoodEnergy, .after = Day_FreeSugars_kcal) %>%
      relocate(Day_Fat_PropFoodEnergy, .after = Day_Fat_kcal) %>%
      relocate(Day_SatFat_PropFoodEnergy, .after = Day_SatFat_kcal) %>%
      relocate(Day_TransFat_PropFoodEnergy, .after = Day_TransFat_kcal) %>%
      relocate(Day_Protein_PropFoodEnergy, .after = Day_Protein_kcal)
```

## Energy Density
```{r}
df.intake24_recall <- df.intake24_recall %>%
      mutate(Day_EnergyDensity = (Day_FoodMilkEnergy/Day_FoodMilkGrams)*100) %>%
      relocate(Day_EnergyDensity, .after = Day_FoodMilkGrams)
```

## **TO UPDATE** Clean high and low energy recalls
```{r eval=FALSE}
#create a subset of recalls where kcals are less than 400
low_kcal <- df.intake24_recall %>%
  filter(Day_Energykcal <= 400)

#create a subset for recalls where kcal are more than 4000
high_kcal <- df.intake24_recall %>%
  filter(Day_Energykcal >= 4000)

#join summed variables to intake24, keeping only those IDs and RecallNo that are in both datasets
high_kcal_items <- inner_join(df.intake24_item, high_kcal, by = c("UserID","HouseholdID", "RecallNo", "Sex","Ethnicity","Age", "age_cat","simd_quintile", "NumberOfRecalls"))
low_kcal_items <- inner_join(df.intake24_item, low_kcal, by = c("UserID","HouseholdID", "RecallNo", "Sex","Ethnicity","Age", "age_cat","simd_quintile", "NumberOfRecalls"))

#look at all low kcal recalls to help with determining decisions
low_ids <- low_kcal %>%
  select(UserID)

Low_intake_all_recalls <- inner_join(df.intake24_item, low_ids, by = "UserID", relationship = "many-to-many")
Low_intake_all_recalls_1 <- left_join(Low_intake_all_recalls, df.intake24_recall, by = c("UserID","HouseholdID", "RecallNo", "Sex","Ethnicity","Age", "age_cat","simd_quintile", "NumberOfRecalls"))

#export high and low energy intakes
#write.xlsx(high_kcal_items, file = "/Users/ricki/Desktop/DISH_data_cleaning/Output/intake24_high_kcal_all_280824.xlsx")
#write.xlsx(low_kcal_items, file = "/Users/ricki/Desktop/DISH_data_cleaning/Output/intake24_low_kcal_all_280824.xlsx")
#write.xlsx(Low_intake_all_recalls_1, file = "/Users/ricki/Desktop/DISH_data_cleaning/Output/intake24_low_kcal_ids_all_recalls_280824.xlsx")

rm(low_kcal, low_kcal_items, high_kcal, high_kcal_items, low_ids, Low_intake_all_recalls, Low_intake_all_recalls_1)
```

```{r}
#clean low energy outliers

df.intake24_item <- df.intake24_item %>%
  filter(!(UserID == 10002909 & RecallNo == 1))

df.intake24_recall <- df.intake24_recall %>%
  filter(!(UserID == 10002909 & RecallNo == 1))

df.intake24_item <- df.intake24_item %>%
  filter(!UserID == 10006095) #removing both recalls as neither passed quality checks (3rd recall also removed in earlier quality checks)

df.intake24_recall <- df.intake24_recall %>%
  filter(!UserID == 10006095)

df.survey <- df.survey %>%
  filter(!UserID == 10006095)

df.intake24_item <- df.intake24_item %>%
  filter(!(UserID == 10001709 & RecallNo == 3))

df.intake24_recall <- df.intake24_recall %>%
  filter(!(UserID == 10001709 & RecallNo == 3))
```


```{r}
#clean high energy outliers
df.intake24_item <- df.intake24_item %>%
  filter(!(UserID == 10009887 & RecallNo == 1))

df.intake24_recall <- df.intake24_recall %>%
  filter(!(UserID == 10009887 & RecallNo == 1))

  
df.intake24_item <- df.intake24_item %>%
  filter(!(UserID == 10000459 & RecallNo == 1))

df.intake24_recall <- df.intake24_recall %>%
  filter(!(UserID == 10000459 & RecallNo == 1))

  
df.intake24_item <- df.intake24_item %>%
  filter(!UserID == 20002885) #remove participant as all recalls did not pass quality checks

df.intake24_recall <- df.intake24_recall %>%
  filter(!UserID == 20002885)

df.survey <- df.survey %>%
  filter(!UserID == 20002885)



df.intake24_item <- df.intake24_item %>%
  filter(!(UserID == 30000069 & RecallNo == 4))

df.intake24_recall <- df.intake24_recall %>%
  filter(!(UserID == 30000069 & RecallNo == 4))
```

Need to update changed energy intakes below
```{r}


```




# Participant Level Values
## Mean participant nutrient and food group intake (across 1-4 recalls)
```{r}
df.intake24_participant <- df.intake24_recall %>% 
      group_by(UserID) %>%
      summarise(
        HouseholdID = first(HouseholdID),
        psu = first(psu),
        Device_group = first(Device_group),
        Age = first(Age),
        age_cat = first(age_cat),
        Sex = first(Sex),
        age_sex_cat = first(age_sex_cat),
        age_cat_drv = first(age_cat_drv),
        age_sex_cat_drv = first(age_sex_cat_drv),
        Ethnicity = first(Ethnicity),
        simd_quintile = first(simd_quintile),
        Education = first(Education),
        adults_cat = first(adults_cat),
        children_cat = first(children_cat),
        FoodParcels = first(FoodParcels),
        NumberOfRecalls = first(NumberOfRecalls), 
        Avg_Energykcal = mean(Day_Energykcal),
        Avg_FoodEnergy = mean(Day_FoodEnergy),
        Avg_FoodMilkEnergy = mean(Day_FoodMilkEnergy),
        Avg_TotalGrams = mean(Day_TotalGrams),
        Avg_FoodGrams = mean(Day_FoodGrams),
        Avg_FoodMilkGrams = mean(Day_FoodMilkGrams),
        Avg_EnergyDensity = mean(Day_EnergyDensity),
        Avg_Carbohydrateg = mean(Day_Carbohydrateg),
        Avg_Carbs_kcal = mean(Day_Carbs_kcal),
        Avg_Carbs_PropFoodEnergy = mean(Day_Carbs_PropFoodEnergy),
        Avg_FreeSugarsg = mean(Day_FreeSugarsg),
        Avg_FreeSugars_kcal = mean(Day_FreeSugars_kcal),
        Avg_FreeSugars_PropFoodEnergy = mean(Day_FreeSugars_PropFoodEnergy),
        Avg_Fatg = mean(Day_Fatg),
        Avg_Fat_kcal = mean(Day_Fat_kcal),
        Avg_Fat_PropFoodEnergy = mean(Day_Fat_PropFoodEnergy),
        Avg_SatFatg = mean(Day_SatFatg),
        Avg_SatFat_kcal = mean(Day_SatFat_kcal),
        Avg_SatFat_PropFoodEnergy = mean(Day_SatFat_PropFoodEnergy),
        Avg_TransFatg = mean(Day_TransFatg),
        Avg_TransFat_kcal = mean(Day_TransFat_kcal),
        Avg_TransFat_PropFoodEnergy = mean(Day_TransFat_PropFoodEnergy),
        Avg_Proteing = mean(Day_Proteing),
        Avg_Protein_kcal = mean(Day_Protein_kcal),
        Avg_Protein_PropFoodEnergy = mean(Day_Protein_PropFoodEnergy),
        Avg_AOACFibreg = mean(Day_AOACFibreg),
        Avg_Alcoholg = mean(Day_Alcoholg),
        Avg_Alcohol_kcal = mean(Day_Alcohol_kcal),
        Avg_VitaminAug = mean(Day_VitaminAug),
        Avg_Riboflavinmg = mean(Day_Riboflavinmg),
        Avg_Folateug = mean(Day_Folateug),
        Avg_VitaminDug = mean(Day_VitaminDug),
        Avg_VitaminB12ug = mean(Day_VitaminB12ug),
        Avg_VitaminCmg = mean(Day_VitaminCmg),
        Avg_Ironmg = mean(Day_Ironmg),
        Avg_Calciummg = mean(Day_Calciummg),
        Avg_Sodiummg = mean(Day_Sodiummg),
        Avg_Saltg = mean(Day_Saltg),
        Avg_Magnesiummg = mean(Day_Magnesiummg),
        Avg_Potassiummg = mean(Day_Potassiummg),
        Avg_Iodineug = mean(Day_Iodineug),
        Avg_Seleniumug = mean(Day_Seleniumug),
        Avg_Zincmg = mean(Day_Zincmg),
        
        Avg_redmeatg = mean(Day_redmeatg),
        Avg_processedmeatg = mean(Day_processedmeatg),
        Avg_redprocessedmeatg = mean(Day_redprocessedmeatg),
        Avg_oilyfish = mean(Day_oilyfishg),
        Avg_fruitg = mean(Day_fruitg),
        Avg_vegg = mean(Day_vegg),
        Avg_fruitvegg = mean(Day_fruitvegg),
        Avg_fruitjuiceg = mean(Day_fruitjuiceg),
        Avg_ssbg = mean(Day_ssbg),
        Avg_sugarconfecg = mean(Day_sugarconfecg),
        Avg_chocolateconfecg = mean(Day_chocolateconfecg),
        Avg_sweetbiscuitsg = mean(Day_sweetbiscuitsg),
        Avg_savourybiscuitsg = mean(Day_savourybiscuitsg),
        Avg_cakespiesg = mean(Day_cakespiesg),
        Avg_savourysnacksg = mean(Day_savourysnacksg),
        Avg_pizzasg = mean(Day_pizzasg),
        Avg_readymealsg = mean(Day_readymealsg),
        Avg_icecreamg = mean(Day_icecreamg),
        Avg_cerealsg = mean(Day_cerealsg),
        Avg_chipsg = mean(Day_chipsg),
        Avg_yoghurtdairydessertg = mean(Day_yoghurtdairydessertg),
        
        Avg_RRPMg = mean(Day_RRPMg),
        Avg_FV_Beansg = mean(Day_FV_Beansg),
        Avg_FV_Portions_Beans = mean(Day_FV_Portions_Beans),
        Avg_FV_FruitJuiceg = mean(Day_FV_FruitJuiceg),
        Avg_FV_Smoothieg = mean(Day_FV_Smoothieg),
        Avg_FV_JuiceSmoothieg = mean(Day_FV_JuiceSmoothieg),
        Avg_FV_Portions_JuiceSmoothie = mean(Day_FV_Portions_JuiceSmoothie),
        Avg_FV_DriedFruitg = mean(Day_FV_DriedFruitg),
        Avg_FV_Portions_DriedFruit = mean(Day_FV_Portions_DriedFruit),
        Avg_FV_FreshFruitg = mean(Day_FV_FreshFruitg),
        Avg_FV_Portions_FreshFruit = mean(Day_FV_Portions_FreshFruit),
        Avg_FV_Vegg = mean(Day_FV_Vegg),
        Avg_FV_Portions_Veg = mean(Day_FV_Portions_Veg),
        Avg_FV_Portions_Total = mean(Day_FV_Portions_Total),
        Avg_FV_Portions_Total_NoJuiceSmoothie = mean(Day_FV_Portions_Total_NoJuiceSmoothie)) %>%
  ungroup()
```

# **CHECK** Contributions of NDNS food groups to nutrient intake

NDNS Food groups - contributions to energy and free sugar intake
```{r}
# Calculate daily intakes of energy and free sugars from food groups
df.intake24_recall_ndns_fg <- df.intake24_item %>%
  group_by(UserID, RecallNo, MainFoodGroupCode) %>% 
  summarise(
        NumberOfRecalls = first(NumberOfRecalls),
        Day_Energykcal_fg = sum(Energykcal),
        Day_FoodEnergy_fg = sum(FoodEnergy),
        Day_FoodMilkEnergy_fg = sum(FoodMilkEnergy),
        Day_TotalGrams_fg = sum(TotalGrams),
        Day_FoodGrams_fg = sum(FoodGrams),
        Day_FoodMilkGrams_fg = sum(FoodMilkGrams),
        Day_Carbohydrateg_fg = sum(Carbohydrateg),
        Day_Carbs_kcal_fg = sum(Carbs_kcal),
        Day_FreeSugarsg_fg = sum(Freesugarsg), 
        Day_FreeSugars_kcal_fg = sum(Freesugars_kcal),
        Day_Fatg_fg = sum(Fatg),
        Day_Fat_kcal_fg = sum(Fat_kcal),
        Day_SatFatg_fg = sum(Saturatedfattyacidsg),
        Day_SatFat_kcal_fg = sum(SatFat_Kcal),
        Day_TransFatg_fg = sum(Transfattyacidsg),
        Day_TransFat_kcal_fg = sum(TransFat_Kcal),
        Day_Proteing_fg = sum(Proteing),
        Day_Protein_kcal_fg = sum(Protein_kcal),
        Day_Alcoholg_fg = sum(Alcoholg),
        Day_Alcohol_kcal_fg = sum(Alcohol_kcal),
        Day_AOACFibreg_fg = sum(AOACg),
        Day_VitaminAug_fg = sum(VitaminAug),
        Day_Riboflavinmg_fg = sum(Riboflavinmg),
        Day_Folateug_fg = sum(Folateug),
        Day_VitaminDug_fg = sum(VitaminDug),
        Day_VitaminB12ug_fg = sum(VitaminB12ug),
        Day_VitaminCmg_fg = sum(VitaminCmg),
        Day_Ironmg_fg = sum(Ironmg),
        Day_Calciummg_fg = sum(Calciummg),
        Day_Sodiummg_fg = sum(Sodiummg),
        Day_Saltg_fg = sum(Saltg), 
        Day_Magnesiummg_fg = sum(Magnesiummg),
        Day_Potassiummg_fg = sum(Potassiummg),
        Day_Iodineug_fg = sum(Iodineug),
        Day_Seleniumug_fg = sum(Seleniumug),
        Day_Zincmg_fg = sum(Zincmg)) 


```

Create grids
```{r eval=FALSE}
# Create a grid with all possible food category and recall number combinations for each participant
# Need to do this separately for different recall numbers

# 1 recall
df.onerecall <- df.intake24_recall %>%
  filter(NumberOfRecalls == 1)

foodgrid_onerecall <- expand.grid( #create a grid of each combination of the below:
  UserID = unique(df.onerecall$UserID), #take each unique UserID
  RecallNo = unique(df.onerecall$RecallNo), #take each unique RecallNo
  MainFoodGroupCode = factor(1:61)) #create a column of with 1-61 for reporting food groups

# 2 recalls
df.tworecalls <- df.intake24_recall %>%
  filter(NumberOfRecalls == 2)

foodgrid_tworecalls <- expand.grid(
  UserID = unique(df.tworecalls$UserID),
  RecallNo = unique(df.tworecalls$RecallNo),
  MainFoodGroupCode = factor(1:61))

# 3 recalls
df.threerecalls <- df.intake24_recall %>%
  filter(NumberOfRecalls == 3)

foodgrid_threerecalls <- expand.grid(
  UserID = unique(df.threerecalls$UserID),
  RecallNo = unique(df.threerecalls$RecallNo),
  MainFoodGroupCode = factor(1:61))

#4 recalls 
df.fourrecalls <- df.intake24_recall %>%
  filter(NumberOfRecalls == 4)

foodgrid_fourrecalls <- expand.grid(
  UserID = unique(df.fourrecalls$UserID),
  RecallNo = unique(df.threerecalls$RecallNo),
  MainFoodGroupCode = factor(1:61))
```

Combine grids
```{r eval=FALSE}
# Combine expanded grids
foodgroup_grid <- bind_rows(foodgrid_onerecall, foodgrid_tworecalls, foodgrid_threerecalls) %>%
  arrange(UserID, RecallNo) %>%
  mutate(MainFoodGroupCode = as.numeric(MainFoodGroupCode))

# Join daily intakes with expanded grids
df.intake24_recall_ndns_fg <- left_join(foodgroup_grid, df.intake24_recall_ndns_fg, by = c("UserID", "RecallNo", "MainFoodGroupCode")) %>%
  relocate(NumberOfRecalls, .after=UserID)

# Change NA values to 0 
df.intake24_recall_ndns_fg <- df.intake24_recall_ndns_fg %>%
  mutate_all(~ifelse(is.na(.), 0, .))

# Remove datasets no longer needed
rm(foodgrid_onerecall, foodgrid_tworecalls, foodgrid_threerecalls, foodgroup_grid)

```

Calculate mean daily intakes of energy and nutrients from food groups 
```{r eval=FALSE}
# Participant level dataset
df.intake24_participant_ndns_fg <- df.intake24_recall_ndns_fg %>%
  group_by(UserID, MainFoodGroupCode) %>% 
  mutate(
        Avg_Energykcal_fg = sum(Day_Energykcal_fg)/NumberOfRecalls,
        Avg_FoodEnergy_fg = sum(Day_FoodEnergy_fg)/NumberOfRecalls,
        Avg_FoodMilkEnergy_fg = sum(Day_FoodMilkEnergy_fg)/NumberOfRecalls,
        Avg_TotalGrams_fg = sum(Day_TotalGrams_fg)/NumberOfRecalls,
        Avg_FoodGrams_fg = sum(Day_FoodGrams_fg)/NumberOfRecalls,
        Avg_FoodMilkGrams_fg = sum(Day_FoodMilkGrams_fg)/NumberOfRecalls,
        Avg_Carbohydrateg_fg = sum(Day_Carbohydrateg_fg)/NumberOfRecalls,
        Avg_Carbs_kcal_fg = sum(Day_Carbs_kcal_fg)/NumberOfRecalls,
        Avg_FreeSugarsg_fg = sum(Day_FreeSugarsg_fg)/NumberOfRecalls, 
        Avg_FreeSugars_kcal_fg = sum(Day_FreeSugars_kcal_fg)/NumberOfRecalls,
        Avg_Fatg_fg = sum(Day_Fatg_fg)/NumberOfRecalls,
        Avg_Fat_kcal_fg = sum(Day_Fat_kcal_fg)/NumberOfRecalls,
        Avg_SatFatg_fg = sum(Day_SatFatg_fg)/NumberOfRecalls,
        Avg_SatFat_kcal_fg = sum(Day_SatFat_kcal_fg)/NumberOfRecalls,
        Avg_TransFatg_fg = sum(Day_TransFatg_fg)/NumberOfRecalls,
        Avg_TransFat_kcal_fg = sum(Day_TransFat_kcal_fg)/NumberOfRecalls,
        Avg_Proteing_fg = sum(Day_Proteing_fg)/NumberOfRecalls,
        Avg_Protein_kcal_fg = sum(Day_Protein_kcal_fg)/NumberOfRecalls,
        Avg_Alcoholg_fg = sum(Day_Alcoholg_fg)/NumberOfRecalls,
        Avg_Alcohol_kcal_fg = sum(Day_Alcohol_kcal_fg)/NumberOfRecalls,
        Avg_AOACFibreg_fg = sum(Day_AOACFibreg_fg)/NumberOfRecalls,
        Avg_VitaminAug_fg = sum(Day_VitaminAug_fg)/NumberOfRecalls,
        Avg_Riboflavinmg_fg = sum(Day_Riboflavinmg_fg)/NumberOfRecalls,
        Avg_Folateug_fg = sum(Day_Folateug_fg)/NumberOfRecalls,
        Avg_VitaminDug_fg = sum(Day_VitaminDug_fg)/NumberOfRecalls,
        Avg_VitaminB12ug_fg = sum(Day_VitaminB12ug_fg)/NumberOfRecalls,
        Avg_VitaminCmg_fg = sum(Day_VitaminCmg_fg)/NumberOfRecalls,
        Avg_Ironmg_fg = sum(Day_Ironmg_fg)/NumberOfRecalls,
        Avg_Calciummg_fg = sum(Day_Calciummg_fg)/NumberOfRecalls,
        Avg_Sodiummg_fg = sum(Day_Sodiummg_fg)/NumberOfRecalls,
        Avg_Saltg_fg = sum(Day_Saltg_fg)/NumberOfRecalls, 
        Avg_Magnesiummg_fg = sum(Day_Magnesiummg_fg)/NumberOfRecalls,
        Avg_Potassiummg_fg = sum(Day_Potassiummg_fg)/NumberOfRecalls,
        Avg_Iodineug_fg = sum(Day_Iodineug_fg)/NumberOfRecalls,
        Avg_Seleniumug_fg = sum(Day_Seleniumug_fg)/NumberOfRecalls,
        Avg_Zincmg_fg = sum(Day_Zincmg_fg)/NumberOfRecalls) %>%
  ungroup()
```


```{r eval=FALSE}
# Change NA values to 0 
df.intake24_participant_ndns_fg <- df.intake24_participant_ndns_fg %>%
  mutate_all(~ifelse(is.na(.), 0, .))

df.intake24_participant_ndns_fg <- df.intake24_participant_ndns_fg %>%
  mutate_all(~ifelse(is.infinite(.), 0, .))

# Fill in values across food groups in all recalls
df.intake24_participant_ndns_fg <- df.intake24_participant_ndns_fg %>%
  group_by(UserID, MainFoodGroupCode) %>%
  mutate(across(starts_with("Avg_"), ~max(., na.rm = TRUE))) %>%
  ungroup()

# Drop day level variables (as participant level dataset)
df.intake24_participant_ndns_fg <- df.intake24_participant_ndns_fg %>%
  select(-starts_with("Day_"))

#Keep one line per food group per participant
df.intake24_participant_ndns_fg <- df.intake24_participant_ndns_fg %>%
  distinct(UserID, MainFoodGroupCode, .keep_all = TRUE)

```

```{r}
# Add in Main Food Group description variable
    df.intake24_participant_ndns_fg <- df.intake24_participant_ndns_fg %>%
      mutate(MainFoodGroupDesc = case_when(
        MainFoodGroupCode == 1 ~ "Pasta, rice and other miscellaneous cereals",
        MainFoodGroupCode == 2 ~ "White bread",
        MainFoodGroupCode == 3 ~ "Wholemeal bread",
        MainFoodGroupCode == 4 ~ "Other breads",
        MainFoodGroupCode == 5 ~ "High fibre breakfast cereals",
        MainFoodGroupCode == 6 ~ "Other breakfast cereals",
        MainFoodGroupCode == 7 ~ "Biscuits",
        MainFoodGroupCode == 8 ~ "Buns, cakes, pastries and fruit pies",
        MainFoodGroupCode == 9 ~ "Puddings",
        MainFoodGroupCode == 10 ~ "Whole milk",
        MainFoodGroupCode == 11 ~ "Semi-skimmed milk",
        MainFoodGroupCode == 12 ~ "Skimmed milk",
        MainFoodGroupCode == 13 ~ "Other milk and cream",
        MainFoodGroupCode == 14 ~ "Cheese",
        MainFoodGroupCode == 15 ~ "Yogurt, fromage frais and other dairy desserts",
        MainFoodGroupCode == 16 ~ "Eggs and egg dishes",
        MainFoodGroupCode == 17 ~ "Butter",
        MainFoodGroupCode == 18 ~ "Polyunsaturated margarine and oils",
        MainFoodGroupCode == 19 ~ "Low fat spread",
        MainFoodGroupCode == 20 ~ "Margarine and other cooking fats and oils NOT polyunsaturated",
        MainFoodGroupCode == 21 ~ "Reduced fat spread",
        MainFoodGroupCode == 22 ~ "Bacon and ham",
        MainFoodGroupCode == 23 ~ "Beef, veal and dishes",
        MainFoodGroupCode == 24 ~ "Lamb and dishes",
        MainFoodGroupCode == 25 ~ "Pork and dishes",
        MainFoodGroupCode == 26 ~ "Coated chicken and turkey manufactured",
        MainFoodGroupCode == 27 ~ "Chicken and turkey dishes",
        MainFoodGroupCode == 28 ~ "Liver, products and dishes",
        MainFoodGroupCode == 29 ~ "Burgers and kebabs",
        MainFoodGroupCode == 30 ~ "Sausages",
        MainFoodGroupCode == 31 ~ "Meat pies and pastries",
        MainFoodGroupCode == 32 ~ "Other meat and meat products",
        MainFoodGroupCode == 33 ~ "White fish coated or fried",
        MainFoodGroupCode == 34 ~ "Other white fish, shellfish and fish dishes",
        MainFoodGroupCode == 35 ~ "Oily fish",
        MainFoodGroupCode == 36 ~ "Salad and other raw vegetables",
        MainFoodGroupCode == 37 ~ "Vegetables (not raw)",
        MainFoodGroupCode == 38 ~ "Chips, fried and roast potatoes and potato products",
        MainFoodGroupCode == 39 ~ "Other potatoes, potato salads and dishes",
        MainFoodGroupCode == 40 ~ "Fruit",
        MainFoodGroupCode == 41 ~ "Sugars, preserves and sweet spreads",
        MainFoodGroupCode == 42 ~ "Crisps and savoury snacks",
        MainFoodGroupCode == 43 ~ "Sugar confectionery",
        MainFoodGroupCode == 44 ~ "Chocolate confectionery",
        MainFoodGroupCode == 45 ~ "Fruit juice",
        MainFoodGroupCode == 47 ~ "Spirits and liqueurs",
        MainFoodGroupCode == 48 ~ "Wine",
        MainFoodGroupCode == 49 ~ "Beer lager cider and perry",
        MainFoodGroupCode == 50 ~ "Miscellaneous",
        MainFoodGroupCode == 51 ~ "Tea, coffee and water",
        MainFoodGroupCode == 52 ~ "Commercial toddlers foods and drinks",
        MainFoodGroupCode == 53 ~ "Ice cream",
        MainFoodGroupCode == 54 ~ "Dietary supplements",
        MainFoodGroupCode == 55 ~ "Artificial sweeteners",
        MainFoodGroupCode == 56 ~ "Nuts and seeds",
        MainFoodGroupCode == 57 ~ "Soft drinks, not diet",
        MainFoodGroupCode == 58 ~ "Soft drinks, diet",
        MainFoodGroupCode == 59 ~ "Brown, granary and wheatgerm bread",
        MainFoodGroupCode == 60 ~ "1% Milk",
        MainFoodGroupCode == 62 ~ "Sandwiches",
        MainFoodGroupCode == 63 ~ "Other milk and cream DF",                         
        MainFoodGroupCode == 64 ~ "Cheese DF",
        MainFoodGroupCode == 65 ~ "Yogurt, fromage frais and other dairy desserts DF",
        MainFoodGroupCode == 66 ~ "Ice cream DF",
        TRUE ~ NA)) %>%
      relocate(MainFoodGroupDesc, .after = MainFoodGroupCode)
```



# **CHECK** Contributions of Reporting food groups to nutrient intake

Reporting Food groups - contributions to energy and free sugar intake
```{r}
# Calculate daily intakes of energy and free sugars from food groups
df.intake24_recall_fg <- df.intake24_item %>%
  group_by(UserID, RecallNo, ReportingFoodGroupCode) %>% 
  summarise(
    NumberOfRecalls = first(NumberOfRecalls),
    Day_Energy_fg=sum(Energykcal),
    Day_FreeSugars_fg=sum(Freesugarsg),
    Day_Fat_fg = sum(Fatg),
    Day_SatFat_fg = sum(Saturatedfattyacidsg)) 


```

Create grids
```{r eval=FALSE}
# Create a grid with all possible food category and recall number combinations for each participant
# Need to do this separately for different recall numbers

# 1 recall
df.onerecall <- df.intake24_recall %>%
  filter(NumberOfRecalls == 1)

foodgrid_onerecall <- expand.grid( #create a grid of each combination of the below:
  UserID = unique(df.onerecall$UserID), #take each unique UserID
  RecallNo = unique(df.onerecall$RecallNo), #take each unique RecallNo
  ReportingFoodGroupCode = factor(1:19)) #create a column of with 1-19 for reporting food groups

# 2 recalls
df.tworecalls <- df.intake24_recall %>%
  filter(NumberOfRecalls == 2)

foodgrid_tworecalls <- expand.grid(
  UserID = unique(df.tworecalls$UserID),
  RecallNo = unique(df.tworecalls$RecallNo),
  ReportingFoodGroupCode = factor(1:19))

# 3 recalls
df.threerecalls <- df.intake24_recall %>%
  filter(NumberOfRecalls == 3)

foodgrid_threerecalls <- expand.grid(
  UserID = unique(df.threerecalls$UserID),
  RecallNo = unique(df.threerecalls$RecallNo),
  ReportingFoodGroupCode = factor(1:19))

#4 recalls 
df.fourrecalls <- df.intake24_recall %>%
  filter(NumberOfRecalls == 4)

foodgrid_fourrecalls <- expand.grid(
  UserID = unique(df.fourrecalls$UserID),
  RecallNo = unique(df.threerecalls$RecallNo),
  ReportingFoodGroupCode = factor(1:19))
```

Combine grids
```{r eval=FALSE}
# Combine expanded grids
foodgroup_grid <- bind_rows(foodgrid_onerecall, foodgrid_tworecalls, foodgrid_threerecalls) %>%
  arrange(UserID, RecallNo) %>%
  mutate(ReportingFoodGroupCode = as.numeric(ReportingFoodGroupCode))

# Join daily intakes with expanded grids
df.intake24_recall_fg <- left_join(foodgroup_grid, df.intake24_recall_fg, by = c("UserID", "RecallNo", "ReportingFoodGroupCode")) %>%
  relocate(NumberOfRecalls, .after=UserID)

# Change NA values to 0 
df.intake24_recall_fg <- df.intake24_recall_fg %>%
  mutate_all(~ifelse(is.na(.), 0, .))

# Remove datasets no longer needed
rm(foodgrid_onerecall, foodgrid_tworecalls, foodgrid_threerecalls, foodgroup_grid)

```

Calculate mean daily intakes of energy and nutrients from food groups 
```{r eval=FALSE}
# Participant level dataset
df.intake24_participant_fg <- df.intake24_recall_fg %>%
  group_by(UserID, ReportingFoodGroupCode) %>% 
  mutate(
    Avg_Energy_fg =   sum(Day_Energy_fg)/NumberOfRecalls,
    Avg_Fat_fg =  sum(Day_Fat_fg)/NumberOfRecalls,
    Avg_SatFat_fg = sum(Day_SatFat_fg)/NumberOfRecalls,
    Avg_FreeSugars_fg = sum(Day_FreeSugars_fg)/NumberOfRecalls)%>%
  ungroup()

# Change NA values to 0 
df.intake24_participant_fg <- df.intake24_participant_fg %>%
  mutate_all(~ifelse(is.na(.), 0, .))

df.intake24_participant_fg <- df.intake24_participant_fg %>%
  mutate_all(~ifelse(is.infinite(.), 0, .))

# Fill in values across food groups in all recalls
df.intake24_participant_fg <- df.intake24_participant_fg %>%
  group_by(UserID, ReportingFoodGroupCode) %>%
  mutate(across(starts_with("Avg_"), ~max(., na.rm = TRUE))) %>%
  ungroup()

# Drop day level variables (as participant level dataset)
df.intake24_participant_fg <- df.intake24_participant_fg %>%
  select(-starts_with("Day_"))

#Keep one line per food group per participant
df.intake24_participant_fg <- df.intake24_participant_fg %>%
  distinct(UserID, ReportingFoodGroupCode, .keep_all = TRUE)

```

Calculate energy and nutrient contributions from food groups
```{r eval=FALSE}
# Pull out mean daily intakes of energy and free sugars
NutrientIntakes <- subset(df.intake24_participant, select=c(UserID, Avg_Energykcal, Avg_FreeSugarsg, Avg_Fatg, Avg_SatFatg))

# Join with mean daily intakes of energy and free sugars from food groups 
df.intake24_participant_fg <- left_join(NutrientIntakes, df.intake24_participant_fg, by=c("UserID"))

#Calculate nutritional contributions from food categories
df.intake24_participant_fg <- df.intake24_participant_fg %>%
  group_by(UserID, ReportingFoodGroupCode) %>%
  mutate(
    Prop_Energy_fg=(Avg_Energy_fg/Avg_Energykcal)*100,
    Prop_Fat_fg = (Avg_Fat_fg/Avg_Fatg)*100,
    Prop_SatFat_fg = (Avg_SatFat_fg/Avg_SatFatg)*100,
    Prop_FreeSugars_fg=(Avg_FreeSugars_fg/Avg_FreeSugarsg)*100) %>%
  ungroup() %>%
  relocate(ReportingFoodGroupCode, .after=UserID) %>% 
  select(-RecallNo, -NumberOfRecalls, -Avg_Energykcal, -Avg_FreeSugarsg, -Avg_Fatg, -Avg_SatFatg) %>%
  mutate_at(vars(starts_with("Prop_")), ~round(., 2))

# Change NA values to 0 
df.intake24_participant_fg <- df.intake24_participant_fg %>%
  mutate_all(~ifelse(is.na(.), 0, .))

```

Add in Reporting Food Group descriptions
```{r eval=FALSE}
#add in description of reporting food codes
df.intake24_participant_fg <- df.intake24_participant_fg %>%
  mutate(ReportingFoodGroupDesc = case_when(
    ReportingFoodGroupCode == 0 ~ "Other",
    ReportingFoodGroupCode == 1 ~ "Red meat",
    ReportingFoodGroupCode == 2 ~ "Red processed meat",
    ReportingFoodGroupCode == 3 ~ "Oily fish",
    ReportingFoodGroupCode == 4 ~ "Fruit",
    ReportingFoodGroupCode == 5 ~ "Vegetables",
    ReportingFoodGroupCode == 6 ~ "Fruit juice",
    ReportingFoodGroupCode == 7 ~ "Sugar-sweetened beverages",
    ReportingFoodGroupCode == 8 ~ "Sugar confectionery",
    ReportingFoodGroupCode == 9 ~ "Chocolate confectionery",
    ReportingFoodGroupCode == 10 ~ "Sweet biscuits",
    ReportingFoodGroupCode == 11 ~ "Savoury biscuits",
    ReportingFoodGroupCode == 12 ~ "Cakes, pastries and fruit pies",
    ReportingFoodGroupCode == 13 ~ "Crisps and savoury snacks",
    ReportingFoodGroupCode == 14 ~ "Pizzas",
    ReportingFoodGroupCode == 15 ~ "Ready meals",
    ReportingFoodGroupCode == 16 ~ "Ice cream and lollies",
    ReportingFoodGroupCode == 17 ~ "Breakfast cereals",
    ReportingFoodGroupCode == 18 ~ "Chips, fried and roast potatoes and potato products",
    ReportingFoodGroupCode == 19 ~ "Yoghurts, fromage frais, and dairy desserts",
       TRUE ~ NA_character_)) %>%
  relocate(ReportingFoodGroupDesc, .after = ReportingFoodGroupCode)

```

# Adherence to Scottish Dietary Goals
```{r}
## Energy density to be max 125kcal/100g ####
df.intake24_participant <- df.intake24_participant %>%
  mutate(
    SDG_Energy = case_when(
      Avg_EnergyDensity <= 125 ~ 1, 
      Avg_EnergyDensity > 125 ~ 0,
      TRUE ~ NA)) 

## Total fat (max 35% of food energy) ####
df.intake24_participant <- df.intake24_participant %>%
  mutate(
    SDG_Fat = case_when(
      Avg_Fat_PropFoodEnergy <= 35 ~ 1,
      Avg_Fat_PropFoodEnergy > 35 ~ 0,
    TRUE ~ NA)) 

## Saturated fat (max 10% of food energy) ####
df.intake24_participant <- df.intake24_participant %>%
  mutate(
    SDG_SatFat = case_when(
      Avg_SatFat_PropFoodEnergy <= 10 ~ 1,
      Avg_SatFat_PropFoodEnergy > 10 ~ 0,
    TRUE ~ NA)) 

## Trans fat (<1% of food energy) ####
df.intake24_participant <- df.intake24_participant %>%
  mutate(
    SDG_TransFat = case_when(
      Avg_TransFat_PropFoodEnergy < 1 ~ 1,
      Avg_TransFat_PropFoodEnergy >= 1 ~ 0,
    TRUE ~ NA)) 

## Free sugars (max 5% of food energy) ####
df.intake24_participant <- df.intake24_participant %>%
  mutate(
    SDG_FreeSugar = case_when(
      Avg_FreeSugars_PropFoodEnergy <= 5 ~ 1,
      Avg_FreeSugars_PropFoodEnergy > 5 ~ 0,
    TRUE ~ NA)) 

## Carbohydrates (~50% of food energy; created upper/lower limits of 45-55%) ####
df.intake24_participant <- df.intake24_participant %>%
  mutate(
    SDG_Carbs = case_when(
      Avg_Carbs_PropFoodEnergy >= 45 & Avg_Carbs_PropFoodEnergy <= 55 ~ 1,
      Avg_Carbs_PropFoodEnergy < 45 | Avg_Carbs_PropFoodEnergy > 55 ~ 0,
    TRUE ~ NA)) 

## Fibre (2-4y 15g/d; 5-10y 20g/d; 11-15y 25g/d) ####
df.intake24_participant <- df.intake24_participant %>%
  mutate(
    SDG_Fibre = case_when(
      Age >= 2 & Age < 5 & Avg_AOACFibreg >= 15 ~ 1,
      Age >= 2 & Age < 5 & Avg_AOACFibreg < 15 ~ 0,
      Age >= 5 & Age < 11 & Avg_AOACFibreg >= 20 ~ 1,
      Age >= 5 & Age < 11 & Avg_AOACFibreg < 20 ~ 0,
      Age >= 11 & Age < 16 & Avg_AOACFibreg >= 25 ~ 1,
      Age >= 11 & Age < 16 & Avg_AOACFibreg < 25 ~ 0,
    TRUE ~ NA)) 

## Salt (2-3y <2g/d; 4-6y <3g/d; 7-10y <5g/d; 11+y <6g/d) ####
df.intake24_participant <- df.intake24_participant %>%
  mutate(
    SDG_Salt = case_when(
      Age >= 2 & Age < 4 & Avg_Saltg < 2 ~ 1,
      Age >= 2 & Age < 4 & Avg_Saltg >= 2 ~ 0,
      Age >= 4 & Age < 7 & Avg_Saltg < 3 ~ 1,
      Age >= 4 & Age < 7 & Avg_Saltg >= 3 ~ 0,
      Age >= 7 & Age < 11 & Avg_Saltg < 5 ~ 1,
      Age >= 7 & Age < 11 & Avg_Saltg >= 5 ~ 0,
      Age >= 11 & Avg_Saltg < 6 ~ 1,
      Age >= 11 & Avg_Saltg >= 6 ~ 0,
    TRUE ~ NA))

## Vegetables and fruits (>=5 portions/d)
df.intake24_participant <- df.intake24_participant %>%
    mutate(
      SDG_FV = case_when(
        Avg_FV_Portions_Total >= 5 ~ 1,
        Avg_FV_Portions_Total < 5 ~ 0,
      TRUE ~ NA),
      
      SDG_FV_NoJuiceSmoothie = case_when(
        Avg_FV_Portions_Total_NoJuiceSmoothie >= 5 ~ 1,
        Avg_FV_Portions_Total_NoJuiceSmoothie < 5 ~ 0,
        TRUE ~ NA))

## Red and red processed meat (<=70 g/d)
df.intake24_participant <- df.intake24_participant %>%
  mutate(
    SDG_RRPM = case_when(
      Avg_RRPMg <= 70 ~ 1, 
      Avg_RRPMg > 70 ~ 0,
      TRUE ~ NA)) 

## Oily fish
df.survey <- df.survey %>%
  mutate(SDG_oilyfish = case_when(
    AFreqOilyFish %in% c("Never", "Not sure", "Less than once a week") ~ 0,
    TRUE ~ 1
  ))

  # Merge with intake24 participant level dataset
    df.SDG_Fish <- df.survey %>%
        select(UserID, SDG_oilyfish)
      
    df.intake24_participant <- left_join(df.intake24_participant, df.SDG_Fish, by = "UserID")
    
    rm(df.SDG_Fish)

## Add values "Yes" or "No"
df.intake24_participant <- df.intake24_participant %>%
  mutate(across(c(SDG_Energy:SDG_oilyfish),as.factor))

df.intake24_participant <- df.intake24_participant %>%
  mutate(SDG_Energy=fct_recode(SDG_Energy,"Yes"="1", "No"="0"),
         SDG_Fat=fct_recode(SDG_Fat,"Yes"="1", "No"="0"),
         SDG_SatFat=fct_recode(SDG_SatFat,"Yes"="1", "No"="0"),
         SDG_TransFat=fct_recode(SDG_TransFat,"Yes"="1", "No"="0"),
         SDG_FreeSugar=fct_recode(SDG_FreeSugar,"Yes"="1", "No"="0"),
         SDG_Carbs=fct_recode(SDG_Carbs,"Yes"="1", "No"="0"),
         SDG_Fibre=fct_recode(SDG_Fibre,"Yes"="1", "No"="0"),
         SDG_Salt=fct_recode(SDG_Salt,"Yes"="1", "No"="0"),
         SDG_FV=fct_recode(SDG_FV,"Yes"="1", "No"="0"),
         SDG_FV_NoJuiceSmoothie=fct_recode(SDG_FV_NoJuiceSmoothie,"Yes"="1", "No"="0"),
         SDG_RRPM=fct_recode(SDG_RRPM,"Yes"="1", "No"="0"),
         SDG_oilyfish=fct_recode(SDG_oilyfish,"Yes"="1", "No"="0"))
```

# Adherence to RNIs and LRNIs
** 1 = do NOT adhere i.e. below the RNI or below the LRNI
```{r include=FALSE}
# protein
df.intake24_participant <- df.intake24_participant %>%
    mutate(RNI_Protein = case_when(Sex == "Male" & Age >= 1 & Age <= 3 & Avg_Proteing >= 14.5 ~ 0,
                                   Sex == "Male" & Age >= 4 & Age <= 6 & Avg_Proteing >= 19.7 ~ 0,
                                   Sex == "Male" & Age >= 7 & Age <= 10 & Avg_Proteing >= 28.3 ~ 0,
                                   Sex == "Male" & Age >= 11 & Age <= 14 & Avg_Proteing >= 42.1 ~ 0,
                                   Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Proteing >= 55.2 ~ 0,
                                  
                                   Sex == "Male" & Age >= 1 & Age <= 3 & Avg_Proteing < 14.5 ~ 1,
                                   Sex == "Male" & Age >= 4 & Age <= 6 & Avg_Proteing < 19.7 ~ 1,
                                   Sex == "Male" & Age >= 7 & Age <= 10 & Avg_Proteing < 28.3 ~ 1,
                                   Sex == "Male" & Age >= 11 & Age <= 14 & Avg_Proteing < 42.1 ~ 1,
                                   Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Proteing < 55.2 ~ 1,
                                   
                                   Sex == "Female" & Age >= 1 & Age <= 3 & Avg_Proteing >= 14.5 ~ 0,
                                   Sex == "Female" & Age >= 4 & Age <= 6 & Avg_Proteing >= 19.7 ~ 0,
                                   Sex == "Female" & Age >= 7 & Age <= 10 & Avg_Proteing >= 28.3 ~ 0,
                                   Sex == "Female" & Age >= 11 & Age <= 14 & Avg_Proteing >= 41.2 ~ 0,
                                   Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Proteing >= 45.4 ~ 0,
                                  
                                   Sex == "Female" & Age >= 1 & Age <= 3 & Avg_Proteing < 14.5 ~ 1,
                                   Sex == "Female" & Age >= 4 & Age <= 6 & Avg_Proteing < 19.7 ~ 1,
                                   Sex == "Female" & Age >= 7 & Age <= 10 & Avg_Proteing < 28.3 ~ 1,
                                   Sex == "Female" & Age >= 11 & Age <= 14 & Avg_Proteing < 41.2 ~ 1,
                                   Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Proteing < 45.4 ~ 1,
                                   
                                   TRUE ~ NA_integer_),
           
       RNI_prct_Protein = case_when(Sex == "Male" & Age >= 1 & Age <= 3 ~ (Avg_Proteing/14.5)*100,
                                    Sex == "Male" & Age >= 4 & Age <= 6 ~ (Avg_Proteing/19.7)*100,
                                    Sex == "Male" & Age >= 7 & Age <= 10 ~ (Avg_Proteing/28.3)*100,
                                    Sex == "Male" & Age >= 11 & Age <= 14 ~ (Avg_Proteing/42.1)*100,
                                    Sex == "Male" & Age >= 15 & Age <= 18 ~ (Avg_Proteing/55.2)*100,
                                    
                                    Sex == "Female" & Age >= 1 & Age <= 3 ~ (Avg_Proteing/14.5)*100,
                                    Sex == "Female" & Age >= 4 & Age <= 6 ~ (Avg_Proteing/19.7)*100,
                                    Sex == "Female" & Age >= 7 & Age <= 10 ~ (Avg_Proteing/28.3)*100,
                                    Sex == "Female" & Age >= 11 & Age <= 14 ~ (Avg_Proteing/41.2)*100,
                                    Sex == "Female" & Age >= 15 & Age <= 18 ~ (Avg_Proteing/45.4)*100,
                                    
                                     TRUE ~ NA_integer_)
       ) %>%  
  
    relocate(RNI_Protein, RNI_prct_Protein, .after = Avg_Proteing)

# vitamin A
df.intake24_participant <- df.intake24_participant %>%  
    mutate(RNI_VitaminA = case_when(Sex == "Male" & Age >= 1 & Age <= 3 & Avg_VitaminAug >= 400 ~ 0,
                                    Sex == "Male" & Age >= 4 & Age <= 6 & Avg_VitaminAug >= 400 ~ 0,
                                    Sex == "Male" & Age >= 7 & Age <= 10 & Avg_VitaminAug >= 500 ~ 0,
                                    Sex == "Male" & Age >= 11 & Age <= 14 & Avg_VitaminAug >= 600 ~ 0,
                                    Sex == "Male" & Age >= 15 & Age <= 18 & Avg_VitaminAug >= 700 ~ 0,
                                  
                                    Sex == "Male" & Age >= 1 & Age <= 3 & Avg_VitaminAug < 400 ~ 1,
                                    Sex == "Male" & Age >= 4 & Age <= 6 & Avg_VitaminAug < 400 ~ 1,
                                    Sex == "Male" & Age >= 7 & Age <= 10 & Avg_VitaminAug < 500 ~ 1,
                                    Sex == "Male" & Age >= 11 & Age <= 14 & Avg_VitaminAug < 600 ~ 1,
                                    Sex == "Male" & Age >= 15 & Age <= 18 & Avg_VitaminAug < 700 ~ 1,
                                    
                                    Sex == "Female" & Age >= 1 & Age <= 3 & Avg_VitaminAug >= 400 ~ 0,
                                    Sex == "Female" & Age >= 4 & Age <= 6 & Avg_VitaminAug >= 400 ~ 0,
                                    Sex == "Female" & Age >= 7 & Age <= 10 & Avg_VitaminAug >= 500 ~ 0,
                                    Sex == "Female" & Age >= 11 & Age <= 14 & Avg_VitaminAug >= 600 ~ 0,
                                    Sex == "Female" & Age >= 15 & Age <= 18 & Avg_VitaminAug >= 600 ~ 0,
                                  
                                    Sex == "Female" & Age >= 1 & Age <= 3 & Avg_VitaminAug < 400 ~ 1,
                                    Sex == "Female" & Age >= 4 & Age <= 6 & Avg_VitaminAug < 400 ~ 1,
                                    Sex == "Female" & Age >= 7 & Age <= 10 & Avg_VitaminAug < 500 ~ 1,
                                    Sex == "Female" & Age >= 11 & Age <= 14 & Avg_VitaminAug < 600 ~ 1,
                                    Sex == "Female" & Age >= 15 & Age <= 18 & Avg_VitaminAug < 600 ~ 1,
                                    
                                    TRUE ~ NA_integer_),
           
          LRNI_VitaminA = case_when(Sex == "Male" & Age >= 1 & Age <= 3 & Avg_VitaminAug >= 200 ~ 0,
                                    Sex == "Male" & Age >= 4 & Age <= 6 & Avg_VitaminAug >= 200 ~ 0,
                                    Sex == "Male" & Age >= 7 & Age <= 10 & Avg_VitaminAug >= 250 ~ 0,
                                    Sex == "Male" & Age >= 11 & Age <= 14 & Avg_VitaminAug >= 250 ~ 0,
                                    Sex == "Male" & Age >= 15 & Age <= 18 & Avg_VitaminAug >= 300 ~ 0,
                                  
                                    Sex == "Male" & Age >= 1 & Age <= 3 & Avg_VitaminAug < 200 ~ 1,
                                    Sex == "Male" & Age >= 4 & Age <= 6 & Avg_VitaminAug < 200 ~ 1,
                                    Sex == "Male" & Age >= 7 & Age <= 10 & Avg_VitaminAug < 250 ~ 1,
                                    Sex == "Male" & Age >= 11 & Age <= 14 & Avg_VitaminAug < 250 ~ 1,
                                    Sex == "Male" & Age >= 15 & Age <= 18 & Avg_VitaminAug < 300 ~ 1,
                                    
                                    Sex == "Female" & Age >= 1 & Age <= 3 & Avg_VitaminAug >= 200 ~ 0,
                                    Sex == "Female" & Age >= 4 & Age <= 6 & Avg_VitaminAug >= 200 ~ 0,
                                    Sex == "Female" & Age >= 7 & Age <= 10 & Avg_VitaminAug >= 250 ~ 0,
                                    Sex == "Female" & Age >= 11 & Age <= 14 & Avg_VitaminAug >= 250 ~ 0,
                                    Sex == "Female" & Age >= 15 & Age <= 18 & Avg_VitaminAug >= 250 ~ 0,
                                  
                                    Sex == "Female" & Age >= 1 & Age <= 3 & Avg_VitaminAug < 200 ~ 1,
                                    Sex == "Female" & Age >= 4 & Age <= 6 & Avg_VitaminAug < 200 ~ 1,
                                    Sex == "Female" & Age >= 7 & Age <= 10 & Avg_VitaminAug < 250 ~ 1,
                                    Sex == "Female" & Age >= 11 & Age <= 14 & Avg_VitaminAug < 250 ~ 1,
                                    Sex == "Female" & Age >= 15 & Age <= 18 & Avg_VitaminAug < 250 ~ 1,
                                    
                                    TRUE ~ NA_integer_),
          
      RNI_prct_VitaminA = case_when(Sex == "Male" & Age >= 1 & Age <= 3 ~ (Avg_VitaminAug/400)*100,
                                    Sex == "Male" & Age >= 4 & Age <= 6 ~ (Avg_VitaminAug/400)*100,
                                    Sex == "Male" & Age >= 7 & Age <= 10 ~ (Avg_VitaminAug/500)*100,
                                    Sex == "Male" & Age >= 11 & Age <= 14 ~ (Avg_VitaminAug/600)*100,
                                    Sex == "Male" & Age >= 15 & Age <= 18 ~ (Avg_VitaminAug/700)*100,
                                    
                                    Sex == "Female" & Age >= 1 & Age <= 3 ~ (Avg_VitaminAug/400)*100,
                                    Sex == "Female" & Age >= 4 & Age <= 6 ~ (Avg_VitaminAug/400)*100,
                                    Sex == "Female" & Age >= 7 & Age <= 10 ~ (Avg_VitaminAug/500)*100,
                                    Sex == "Female" & Age >= 11 & Age <= 14 ~ (Avg_VitaminAug/600)*100,
                                    Sex == "Female" & Age >= 15 & Age <= 18 ~ (Avg_VitaminAug/600)*100,
                                    
                                     TRUE ~ NA_integer_)
           ) %>%  
  
    relocate(RNI_VitaminA, LRNI_VitaminA, RNI_prct_VitaminA, .after = Avg_VitaminAug)

# riboflavin
df.intake24_participant <- df.intake24_participant %>%  
    mutate(RNI_Riboflavin = case_when(Sex == "Male" & Age >= 1 & Age <= 3 & Avg_Riboflavinmg >= 0.6 ~ 0,
                                      Sex == "Male" & Age >= 4 & Age <= 6 & Avg_Riboflavinmg >= 0.8 ~ 0,
                                      Sex == "Male" & Age >= 7 & Age <= 10 & Avg_Riboflavinmg >= 1.0 ~ 0,
                                      Sex == "Male" & Age >= 11 & Age <= 14 & Avg_Riboflavinmg >= 1.2 ~ 0,
                                      Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Riboflavinmg >= 1.3 ~ 0,
                                  
                                      Sex == "Male" & Age >= 1 & Age <= 3 & Avg_Riboflavinmg < 0.6 ~ 1,
                                      Sex == "Male" & Age >= 4 & Age <= 6 & Avg_Riboflavinmg < 0.8 ~ 1,
                                      Sex == "Male" & Age >= 7 & Age <= 10 & Avg_Riboflavinmg < 1.0 ~ 1,
                                      Sex == "Male" & Age >= 11 & Age <= 14 & Avg_Riboflavinmg < 1.2 ~ 1,
                                      Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Riboflavinmg < 1.3 ~ 1,
                                      
                                      Sex == "Female" & Age >= 1 & Age <= 3 & Avg_Riboflavinmg >= 0.6 ~ 0,
                                      Sex == "Female" & Age >= 4 & Age <= 6 & Avg_Riboflavinmg >= 0.8 ~ 0,
                                      Sex == "Female" & Age >= 7 & Age <= 10 & Avg_Riboflavinmg >= 1.0 ~ 0,
                                      Sex == "Female" & Age >= 11 & Age <= 14 & Avg_Riboflavinmg >= 1.1 ~ 0,
                                      Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Riboflavinmg >= 1.1 ~ 0,
                                  
                                      Sex == "Female" & Age >= 1 & Age <= 3 & Avg_Riboflavinmg < 0.6 ~ 1,
                                      Sex == "Female" & Age >= 4 & Age <= 6 & Avg_Riboflavinmg < 0.8 ~ 1,
                                      Sex == "Female" & Age >= 7 & Age <= 10 & Avg_Riboflavinmg < 1.0 ~ 1,
                                      Sex == "Female" & Age >= 11 & Age <= 14 & Avg_Riboflavinmg < 1.1 ~ 1,
                                      Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Riboflavinmg < 1.1 ~ 1,
                                      
                                      TRUE ~ NA_integer_),
           
          LRNI_Riboflavin = case_when(Sex == "Male" & Age >= 1 & Age <= 3 & Avg_Riboflavinmg >= 0.3 ~ 0,
                                      Sex == "Male" & Age >= 4 & Age <= 6 & Avg_Riboflavinmg >= 0.4 ~ 0,
                                      Sex == "Male" & Age >= 7 & Age <= 10 & Avg_Riboflavinmg >= 0.5 ~ 0,
                                      Sex == "Male" & Age >= 11 & Age <= 14 & Avg_Riboflavinmg >= 0.8 ~ 0,
                                      Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Riboflavinmg >= 0.8 ~ 0,
                                  
                                      Sex == "Male" & Age >= 1 & Age <= 3 & Avg_Riboflavinmg < 0.3 ~ 1,
                                      Sex == "Male" & Age >= 4 & Age <= 6 & Avg_Riboflavinmg < 0.4 ~ 1,
                                      Sex == "Male" & Age >= 7 & Age <= 10 & Avg_Riboflavinmg < 0.5 ~ 1,
                                      Sex == "Male" & Age >= 11 & Age <= 14 & Avg_Riboflavinmg < 0.8 ~ 1,
                                      Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Riboflavinmg < 0.8 ~ 1,
                                      
                                      Sex == "Female" & Age >= 1 & Age <= 3 & Avg_Riboflavinmg >= 0.3 ~ 0,
                                      Sex == "Female" & Age >= 4 & Age <= 6 & Avg_Riboflavinmg >= 0.4 ~ 0,
                                      Sex == "Female" & Age >= 7 & Age <= 10 & Avg_Riboflavinmg >= 0.5 ~ 0,
                                      Sex == "Female" & Age >= 11 & Age <= 14 & Avg_Riboflavinmg >= 0.8 ~ 0,
                                      Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Riboflavinmg >= 0.8 ~ 0,
                                  
                                      Sex == "Female" & Age >= 1 & Age <= 3 & Avg_Riboflavinmg < 0.3 ~ 1,
                                      Sex == "Female" & Age >= 4 & Age <= 6 & Avg_Riboflavinmg < 0.4 ~ 1,
                                      Sex == "Female" & Age >= 7 & Age <= 10 & Avg_Riboflavinmg < 0.5 ~ 1,
                                      Sex == "Female" & Age >= 11 & Age <= 14 & Avg_Riboflavinmg < 0.8 ~ 1,
                                      Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Riboflavinmg < 0.8 ~ 1,
                                      
                                      TRUE ~ NA_integer_),
          
      RNI_prct_Riboflavin = case_when(Sex == "Male" & Age >= 1 & Age <= 3 ~ (Avg_Riboflavinmg/0.6)*100,
                                      Sex == "Male" & Age >= 4 & Age <= 6 ~ (Avg_Riboflavinmg/0.8)*100,
                                      Sex == "Male" & Age >= 7 & Age <= 10 ~ (Avg_Riboflavinmg/1.0)*100,
                                      Sex == "Male" & Age >= 11 & Age <= 14 ~ (Avg_Riboflavinmg/1.2)*100,
                                      Sex == "Male" & Age >= 15 & Age <= 18 ~ (Avg_Riboflavinmg/1.3)*100,
      
                                      Sex == "Female" & Age >= 1 & Age <= 3 ~ (Avg_Riboflavinmg/0.6)*100,
                                      Sex == "Female" & Age >= 4 & Age <= 6 ~ (Avg_Riboflavinmg/0.8)*100,
                                      Sex == "Female" & Age >= 7 & Age <= 10 ~ (Avg_Riboflavinmg/1.0)*100,
                                      Sex == "Female" & Age >= 11 & Age <= 14 ~ (Avg_Riboflavinmg/1.1)*100,
                                      Sex == "Female" & Age >= 15 & Age <= 18 ~ (Avg_Riboflavinmg/1.1)*100,
                                    
                                     TRUE ~ NA_integer_)
           ) %>%  
  
    relocate(RNI_Riboflavin, LRNI_Riboflavin, RNI_prct_Riboflavin, .after = Avg_Riboflavinmg)

# folate - no differences between males and females
df.intake24_participant <- df.intake24_participant %>%  
    mutate(RNI_Folate = case_when(Age >= 1 & Age <= 3 & Avg_Folateug >= 70 ~ 0,
                                  Age >= 4 & Age <= 6 & Avg_Folateug >= 100 ~ 0,
                                  Age >= 7 & Age <= 10 & Avg_Folateug >= 150 ~ 0,
                                  Age >= 11 & Age <= 14 & Avg_Folateug >= 200 ~ 0,
                                  Age >= 15 & Age <= 18 & Avg_Folateug >= 200 ~ 0,
                                  
                                  Age >= 1 & Age <= 3 & Avg_Folateug < 70 ~ 1,
                                  Age >= 4 & Age <= 6 & Avg_Folateug < 100 ~ 1,
                                  Age >= 7 & Age <= 10 & Avg_Folateug < 150 ~ 1,
                                  Age >= 11 & Age <= 14 & Avg_Folateug < 200 ~ 1,
                                  Age >= 15 & Age <= 18 & Avg_Folateug < 200 ~ 1,
                                  
                                  TRUE ~ NA_integer_),
           
          LRNI_Folate = case_when(Age >= 1 & Age <= 3 & Avg_Folateug >= 35 ~ 0,
                                  Age >= 4 & Age <= 6 & Avg_Folateug >= 50 ~ 0,
                                  Age >= 7 & Age <= 10 & Avg_Folateug >= 75 ~ 0,
                                  Age >= 11 & Age <= 14 & Avg_Folateug >= 100 ~ 0,
                                  Age >= 15 & Age <= 18 & Avg_Folateug >= 100 ~ 0,
                                  
                                  Age >= 1 & Age <= 3 & Avg_Folateug < 35 ~ 1,
                                  Age >= 4 & Age <= 6 & Avg_Folateug < 50 ~ 1,
                                  Age >= 7 & Age <= 10 & Avg_Folateug < 75 ~ 1,
                                  Age >= 11 & Age <= 14 & Avg_Folateug < 100 ~ 1,
                                  Age >= 15 & Age <= 18 & Avg_Folateug < 100 ~ 1,
                                  
                                  TRUE ~ NA_integer_),
          
      RNI_prct_Folate = case_when(Age >= 1 & Age <= 3 ~ (Avg_Folateug/70)*100,
                                  Age >= 4 & Age <= 6 ~ (Avg_Folateug/100)*100,
                                  Age >= 7 & Age <= 10 ~ (Avg_Folateug/150)*100,
                                  Age >= 11 & Age <= 14 ~ (Avg_Folateug/200)*100,
                                  Age >= 15 & Age <= 18 ~ (Avg_Folateug/200)*100,
                                  
                                  TRUE ~ NA_real_)
           ) %>%  
  
    relocate(RNI_Folate, LRNI_Folate, RNI_prct_Folate, .after = Avg_Folateug)

# vitamin D - no differences between males and females
df.intake24_participant <- df.intake24_participant %>%  
    mutate(RNI_VitaminD = case_when(Age >= 1 & Age <= 3 & Avg_VitaminDug >= 10 ~ 0,
                                    Age >= 4 & Age <= 6 & Avg_VitaminDug >= 10 ~ 0,
                                    Age >= 7 & Age <= 10 & Avg_VitaminDug >= 10 ~ 0,
                                    Age >= 11 & Age <= 14 & Avg_VitaminDug >= 10 ~ 0,
                                    Age >= 15 & Age <= 18 & Avg_VitaminDug >= 10 ~ 0,
                                  
                                    Age >= 1 & Age <= 3 & Avg_VitaminDug < 10 ~ 1,
                                    Age >= 4 & Age <= 6 & Avg_VitaminDug < 10 ~ 1,
                                    Age >= 7 & Age <= 10 & Avg_VitaminDug < 10 ~ 1,
                                    Age >= 11 & Age <= 14 & Avg_VitaminDug < 10 ~ 1,
                                    Age >= 15 & Age <= 18 & Avg_VitaminDug < 10 ~ 1,
                                    TRUE ~ NA_integer_),
          
      RNI_prct_VitaminD = case_when(Age >= 1 & Age <= 3 ~ (Avg_VitaminDug/10)*100,
                                    Age >= 4 & Age <= 6 ~ (Avg_VitaminDug/10)*100,
                                    Age >= 7 & Age <= 10 ~ (Avg_VitaminDug/10)*100,
                                    Age >= 11 & Age <= 14 ~ (Avg_VitaminDug/10)*100,
                                    Age >= 15 & Age <= 18 ~ (Avg_VitaminDug/10)*100,
                                    
                                    TRUE ~ NA_integer_)
           ) %>%  
  
    relocate(RNI_VitaminD, RNI_prct_VitaminD, .after = Avg_VitaminDug)

# vitamin b12 - no differences between males and females
df.intake24_participant <- df.intake24_participant %>%  
    mutate(RNI_VitaminB12 = case_when(Age >= 1 & Age <= 3 & Avg_VitaminB12ug >= 0.5 ~ 0,
                                      Age >= 4 & Age <= 6 & Avg_VitaminB12ug >= 0.8 ~ 0,
                                      Age >= 7 & Age <= 10 & Avg_VitaminB12ug >= 1.0 ~ 0,
                                      Age >= 11 & Age <= 14 & Avg_VitaminB12ug >= 1.2 ~ 0,
                                      Age >= 15 & Age <= 18 & Avg_VitaminB12ug >= 1.5 ~ 0,
                                      
                                      Age >= 1 & Age <= 3 & Avg_VitaminB12ug < 0.5 ~ 1,
                                      Age >= 4 & Age <= 6 & Avg_VitaminB12ug < 0.8 ~ 1,
                                      Age >= 7 & Age <= 10 & Avg_VitaminB12ug < 1.0 ~ 1,
                                      Age >= 11 & Age <= 14 & Avg_VitaminB12ug < 1.2 ~ 1,
                                      Age >= 15 & Age <= 18 & Avg_VitaminB12ug < 1.5 ~ 1,
                                      
                                      TRUE ~ NA_integer_),
           
           LRNI_VitaminB12 = case_when(Age >= 1 & Age <= 3 & Avg_VitaminB12ug >= 0.3 ~ 0, 
                                       Age >= 4 & Age <= 6 & Avg_VitaminB12ug >= 0.5 ~ 0,
                                       Age >= 7 & Age <= 10 & Avg_VitaminB12ug >= 0.6 ~ 0,
                                       Age >= 11 & Age <= 14 & Avg_VitaminB12ug >= 0.8 ~ 0,
                                       Age >= 15 & Age <=18 & Avg_VitaminB12ug >= 1.0 ~ 0,
                                       
                                       Age >= 1 & Age <= 3 & Avg_VitaminB12ug < 0.3 ~ 1,
                                       Age >= 4 & Age <= 6 & Avg_VitaminB12ug < 0.5 ~ 1,
                                       Age >= 7 & Age <= 10 & Avg_VitaminB12ug < 0.6 ~ 1,
                                       Age >= 11 & Age <= 14 & Avg_VitaminB12ug < 0.8 ~ 1,
                                       Age >= 15 & Age <=18 & Avg_VitaminB12ug < 1.0 ~ 1,
                                       
                                       TRUE ~ NA_integer_),
                     
      RNI_prct_VitaminB12 = case_when(Age >= 1 & Age <= 3 ~ (Avg_VitaminB12ug/0.5)*100,
                                      Age >= 4 & Age <= 6 ~ (Avg_VitaminB12ug/0.8)*100,
                                      Age >= 7 & Age <= 10 ~ (Avg_VitaminB12ug/1.0)*100,
                                      Age >= 11 & Age <= 14 ~ (Avg_VitaminB12ug/1.2)*100,
                                      Age >= 15 & Age <= 18 ~ (Avg_VitaminB12ug/1.5)*100,
      
                                      TRUE ~ NA_integer_)
           ) %>%  
  
    relocate(RNI_VitaminB12, LRNI_VitaminB12, RNI_prct_VitaminB12, .after = Avg_VitaminB12ug)

# vitamin C - no differences between males and females
df.intake24_participant <- df.intake24_participant %>%  
    mutate(RNI_VitaminC = case_when(Age >= 1 & Age <= 10 & Avg_VitaminCmg >= 30 ~ 0,
                                    Age >= 11 & Age <= 14 & Avg_VitaminCmg >= 35 ~ 0,
                                    Age >= 15 & Age <= 18 & Avg_VitaminCmg >= 40 ~ 0,
                                    
                                    Age >= 1 & Age <= 10 & Avg_VitaminCmg < 30 ~ 1,
                                    Age >= 11 & Age <= 14 & Avg_VitaminCmg < 35 ~ 1,
                                    Age >= 15 & Age <= 18 & Avg_VitaminCmg < 40 ~ 1,
                                      
                                      TRUE ~ NA_integer_),
           
           LRNI_VitaminC = case_when(Age >= 1 & Age <= 10 & Avg_VitaminCmg >= 8 ~ 0, 
                                       Age >= 11 & Age <= 14 & Avg_VitaminCmg >= 9 ~ 0,
                                       Age >= 15 & Age <= 18 & Avg_VitaminCmg >= 10 ~ 0,
                                       
                                       Age >= 1 & Age <= 10 & Avg_VitaminCmg < 8 ~ 1,
                                       Age >= 11 & Age <= 14 & Avg_VitaminCmg < 9 ~ 1,
                                       Age >= 15 & Age <= 18 & Avg_VitaminCmg < 10 ~ 1,
                                       
                                       TRUE ~ NA_integer_),
                     
      RNI_prct_VitaminC = case_when(Age >= 1 & Age <= 10 ~ (Avg_VitaminCmg/30)*100,
                                    Age >= 11 & Age <= 14 ~ (Avg_VitaminCmg/35)*100,
                                    Age >= 15 & Age <= 18 ~ (Avg_VitaminCmg/40)*100,
      
                                    TRUE ~ NA_integer_)
           ) %>%  
  
    relocate(RNI_VitaminC, LRNI_VitaminC, RNI_prct_VitaminC, .after = Avg_VitaminCmg)

# iron    
df.intake24_participant <- df.intake24_participant %>%
    mutate(RNI_Iron = case_when(Sex == "Male" & Age >= 1 & Age <= 3 & Avg_Ironmg >= 6.9 ~ 0,
                                Sex == "Male" & Age >= 4 & Age <= 6 & Avg_Ironmg >= 6.1 ~ 0,
                                Sex == "Male" & Age >= 7 & Age <= 10 & Avg_Ironmg >= 8.7 ~ 0,
                                Sex == "Male" & Age >= 11 & Age <= 14 & Avg_Ironmg >= 11.3 ~ 0,
                                Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Ironmg >= 11.3 ~ 0,
                                  
                                Sex == "Male" & Age >= 1 & Age <= 3 & Avg_Ironmg < 6.9 ~ 1,
                                Sex == "Male" & Age >= 4 & Age <= 6 & Avg_Ironmg < 6.1 ~ 1,
                                Sex == "Male" & Age >= 7 & Age <= 10 & Avg_Ironmg < 8.7 ~ 1,
                                Sex == "Male" & Age >= 11 & Age <= 14 & Avg_Ironmg < 11.3 ~ 1,
                                Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Ironmg < 11.3 ~ 1,
                                      
                                Sex == "Female" & Age >= 1 & Age <= 3 & Avg_Ironmg >= 6.9 ~ 0,
                                Sex == "Female" & Age >= 4 & Age <= 6 & Avg_Ironmg >= 6.1 ~ 0,
                                Sex == "Female" & Age >= 7 & Age <= 10 & Avg_Ironmg >= 8.7 ~ 0,
                                Sex == "Female" & Age >= 11 & Age <= 14 & Avg_Ironmg >= 14.8 ~ 0,
                                Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Ironmg >= 14.8 ~ 0,
                                      
                                Sex == "Female" & Age >= 1 & Age <= 3 & Avg_Ironmg < 6.9 ~ 1,
                                Sex == "Female" & Age >= 4 & Age <= 6 & Avg_Ironmg < 6.1 ~ 1,
                                Sex == "Female" & Age >= 7 & Age <= 10 & Avg_Ironmg < 8.7 ~ 1,
                                Sex == "Female" & Age >= 11 & Age <= 14 & Avg_Ironmg < 14.8 ~ 1,
                                Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Ironmg < 14.8 ~ 1,
                                      
                                TRUE ~ NA_integer_),
           
          LRNI_Iron = case_when(Sex == "Male" & Age >= 1 & Age <= 3 & Avg_Ironmg >= 3.7 ~ 0,
                                Sex == "Male" & Age >= 4 & Age <= 6 & Avg_Ironmg >= 3.3 ~ 0,
                                Sex == "Male" & Age >= 7 & Age <= 10 & Avg_Ironmg >= 4.7 ~ 0,
                                Sex == "Male" & Age >= 11 & Age <= 14 & Avg_Ironmg >= 6.1 ~ 0,
                                Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Ironmg >= 6.1 ~ 0,
                                  
                                Sex == "Male" & Age >= 1 & Age <= 3 & Avg_Ironmg < 3.7 ~ 1,
                                Sex == "Male" & Age >= 4 & Age <= 6 & Avg_Ironmg < 3.3 ~ 1,
                                Sex == "Male" & Age >= 7 & Age <= 10 & Avg_Ironmg < 4.7 ~ 1,
                                Sex == "Male" & Age >= 11 & Age <= 14 & Avg_Ironmg < 6.1 ~ 1,
                                Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Ironmg < 6.1 ~ 1,
                                      
                                Sex == "Female" & Age >= 1 & Age <= 3 & Avg_Ironmg >= 3.7 ~ 0,
                                Sex == "Female" & Age >= 4 & Age <= 6 & Avg_Ironmg >= 3.3 ~ 0,
                                Sex == "Female" & Age >= 7 & Age <= 10 & Avg_Ironmg >= 4.7 ~ 0,
                                Sex == "Female" & Age >= 11 & Age <= 14 & Avg_Ironmg >= 8.0 ~ 0,
                                Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Ironmg >= 8.0 ~ 0,
                                  
                                Sex == "Female" & Age >= 1 & Age <= 3 & Avg_Ironmg < 3.7 ~ 1,
                                Sex == "Female" & Age >= 4 & Age <= 6 & Avg_Ironmg < 3.3 ~ 1,
                                Sex == "Female" & Age >= 7 & Age <= 10 & Avg_Ironmg < 4.7 ~ 1,
                                Sex == "Female" & Age >= 11 & Age <= 14 & Avg_Ironmg < 8.0 ~ 1,
                                Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Ironmg < 8.0 ~ 1,
                                      
                                TRUE ~ NA_integer_),
          
      RNI_prct_Iron = case_when(Sex == "Male" & Age >= 1 & Age <= 3 ~ (Avg_Ironmg/6.9)*100,
                                Sex == "Male" & Age >= 4 & Age <= 6 ~ (Avg_Ironmg/6.1)*100,
                                Sex == "Male" & Age >= 7 & Age <= 10 ~ (Avg_Ironmg/8.7)*100,
                                Sex == "Male" & Age >= 11 & Age <= 14 ~ (Avg_Ironmg/11.3)*100,
                                Sex == "Male" & Age >= 15 & Age <= 18 ~ (Avg_Ironmg/11.3)*100,
      
                                Sex == "Female" & Age >= 1 & Age <= 3 ~ (Avg_Ironmg/6.9)*100,
                                Sex == "Female" & Age >= 4 & Age <= 6 ~ (Avg_Ironmg/6.1)*100,
                                Sex == "Female" & Age >= 7 & Age <= 10 ~ (Avg_Ironmg/8.7)*100,
                                Sex == "Female" & Age >= 11 & Age <= 14 ~ (Avg_Ironmg/14.8)*100,
                                Sex == "Female" & Age >= 15 & Age <= 18 ~ (Avg_Ironmg/14.8)*100,
      
                                TRUE ~ NA_integer_)
           ) %>%  
  
    relocate(RNI_Iron, LRNI_Iron, RNI_prct_Iron, .after = Avg_Ironmg)

# calcium   
df.intake24_participant <- df.intake24_participant %>%
    mutate(RNI_Calcium = case_when(Sex == "Male" & Age >= 1 & Age <= 3 & Avg_Calciummg >= 350 ~ 0,
                                   Sex == "Male" & Age >= 4 & Age <= 6 & Avg_Calciummg >= 450 ~ 0,
                                   Sex == "Male" & Age >= 7 & Age <= 10 & Avg_Calciummg >= 550 ~ 0,
                                   Sex == "Male" & Age >= 11 & Age <= 14 & Avg_Calciummg >= 1000 ~ 0,
                                   Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Calciummg >= 1000 ~ 0,
                                    
                                   Sex == "Male" & Age >= 1 & Age <= 3 & Avg_Calciummg < 350 ~ 1,
                                   Sex == "Male" & Age >= 4 & Age <= 6 & Avg_Calciummg < 450 ~ 1,
                                   Sex == "Male" & Age >= 7 & Age <= 10 & Avg_Calciummg < 550 ~ 1,
                                   Sex == "Male" & Age >= 11 & Age <= 14 & Avg_Calciummg < 1000 ~ 1,
                                   Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Calciummg < 1000 ~ 1,
                                        
                                   Sex == "Female" & Age >= 1 & Age <= 3 & Avg_Calciummg >= 350 ~ 0,
                                   Sex == "Female" & Age >= 4 & Age <= 6 & Avg_Calciummg >= 450 ~ 0,
                                   Sex == "Female" & Age >= 7 & Age <= 10 & Avg_Calciummg >= 550 ~ 0,
                                   Sex == "Female" & Age >= 11 & Age <= 14 & Avg_Calciummg >= 800 ~ 0,
                                   Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Calciummg >= 800 ~ 0,
                                        
                                   Sex == "Female" & Age >= 1 & Age <= 3 & Avg_Calciummg < 350 ~ 1,
                                   Sex == "Female" & Age >= 4 & Age <= 6 & Avg_Calciummg < 450 ~ 1,
                                   Sex == "Female" & Age >= 7 & Age <= 10 & Avg_Calciummg < 550 ~ 1,
                                   Sex == "Female" & Age >= 11 & Age <= 14 & Avg_Calciummg < 800 ~ 1,
                                   Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Calciummg < 800 ~ 1,
                                        
                                   TRUE ~ NA_integer_),
           
          LRNI_Calcium = case_when(Sex == "Male" & Age >= 1 & Age <= 3 & Avg_Calciummg >= 200 ~ 0,
                                Sex == "Male" & Age >= 4 & Age <= 6 & Avg_Calciummg >= 275 ~ 0,
                                Sex == "Male" & Age >= 7 & Age <= 10 & Avg_Calciummg >= 325 ~ 0,
                                Sex == "Male" & Age >= 11 & Age <= 14 & Avg_Calciummg >= 480 ~ 0,
                                Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Calciummg >= 480 ~ 0,
                                  
                                Sex == "Male" & Age >= 1 & Age <= 3 & Avg_Calciummg < 200 ~ 1,
                                Sex == "Male" & Age >= 4 & Age <= 6 & Avg_Calciummg < 275 ~ 1,
                                Sex == "Male" & Age >= 7 & Age <= 10 & Avg_Calciummg < 325 ~ 1,
                                Sex == "Male" & Age >= 11 & Age <= 14 & Avg_Calciummg < 480 ~ 1,
                                Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Calciummg < 480 ~ 1,
                                      
                                Sex == "Female" & Age >= 1 & Age <= 3 & Avg_Calciummg >= 200 ~ 0,
                                Sex == "Female" & Age >= 4 & Age <= 6 & Avg_Calciummg >= 275 ~ 0,
                                Sex == "Female" & Age >= 7 & Age <= 10 & Avg_Calciummg >= 325 ~ 0,
                                Sex == "Female" & Age >= 11 & Age <= 14 & Avg_Calciummg >= 450 ~ 0,
                                Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Calciummg >= 450 ~ 0,
                                  
                                Sex == "Female" & Age >= 1 & Age <= 3 & Avg_Calciummg < 200 ~ 1,
                                Sex == "Female" & Age >= 4 & Age <= 6 & Avg_Calciummg < 275 ~ 1,
                                Sex == "Female" & Age >= 7 & Age <= 10 & Avg_Calciummg < 325 ~ 1,
                                Sex == "Female" & Age >= 11 & Age <= 14 & Avg_Calciummg < 450 ~ 1,
                                Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Calciummg < 450 ~ 1,
                                      
                                TRUE ~ NA_integer_),
          
      RNI_prct_Calcium = case_when(Sex == "Male" & Age >= 1 & Age <= 3 ~ (Avg_Calciummg/350)*100,
                                   Sex == "Male" & Age >= 4 & Age <= 6 ~ (Avg_Calciummg/450)*100,
                                   Sex == "Male" & Age >= 7 & Age <= 10 ~ (Avg_Calciummg/550)*100,
                                   Sex == "Male" & Age >= 11 & Age <= 14 ~ (Avg_Calciummg/1000)*100,
                                   Sex == "Male" & Age >= 15 & Age <= 18 ~ (Avg_Calciummg/1000)*100,
        
                                   Sex == "Female" & Age >= 1 & Age <= 3 ~ (Avg_Calciummg/350)*100,
                                   Sex == "Female" & Age >= 4 & Age <= 6 ~ (Avg_Calciummg/450)*100,
                                   Sex == "Female" & Age >= 7 & Age <= 10 ~ (Avg_Calciummg/550)*100,
                                   Sex == "Female" & Age >= 11 & Age <= 14 ~ (Avg_Calciummg/800)*100,
                                   Sex == "Female" & Age >= 15 & Age <= 18 ~ (Avg_Calciummg/800)*100,
        
                                   TRUE ~ NA_integer_)
           ) %>%  
  
    relocate(RNI_Calcium, LRNI_Calcium, RNI_prct_Calcium, .after = Avg_Calciummg)

# magnesium - no differences between males and females
df.intake24_participant <- df.intake24_participant %>%  
    mutate(RNI_Magnesium = case_when(Age >= 1 & Age <= 3 & Avg_Magnesiummg >= 85 ~ 0,
                                     Age >= 4 & Age <= 6 & Avg_Magnesiummg >= 120 ~ 0,
                                     Age >= 7 & Age <= 10 & Avg_Magnesiummg >= 200 ~ 0,
                                     Age >= 11 & Age <= 14 & Avg_Magnesiummg >= 280 ~ 0,
                                     Age >= 15 & Age <= 18 & Avg_Magnesiummg >= 300 ~ 0,
                                      
                                     Age >= 1 & Age <= 3 & Avg_Magnesiummg < 85 ~ 1,
                                     Age >= 4 & Age <= 6 & Avg_Magnesiummg < 120 ~ 1,
                                     Age >= 7 & Age <= 10 & Avg_Magnesiummg < 200 ~ 1,
                                     Age >= 11 & Age <= 14 & Avg_Magnesiummg < 280 ~ 1,
                                     Age >= 15 & Age <= 18 & Avg_Magnesiummg < 300 ~ 1,
                                      
                                     TRUE ~ NA_integer_),
           
           LRNI_Magnesium = case_when(Age >= 1 & Age <= 3 & Avg_Magnesiummg >= 50 ~ 0, 
                                      Age >= 4 & Age <= 6 & Avg_Magnesiummg >= 70 ~ 0,
                                      Age >= 7 & Age <= 10 & Avg_Magnesiummg >= 115 ~ 0,
                                      Age >= 11 & Age <= 14 & Avg_Magnesiummg >= 180 ~ 0,
                                      Age >= 15 & Age <=18 & Avg_Magnesiummg >= 190 ~ 0,
                                       
                                      Age >= 1 & Age <= 3 & Avg_Magnesiummg < 50 ~ 1,
                                      Age >= 4 & Age <= 6 & Avg_Magnesiummg < 70 ~ 1,
                                      Age >= 7 & Age <= 10 & Avg_Magnesiummg < 115 ~ 1,
                                      Age >= 11 & Age <= 14 & Avg_Magnesiummg < 180 ~ 1,
                                      Age >= 15 & Age <=18 & Avg_Magnesiummg < 190 ~ 1,
                                       
                                      TRUE ~ NA_integer_),
                     
      RNI_prct_Magnesium = case_when(Age >= 1 & Age <= 3 ~ (Avg_Magnesiummg/85)*100,
                                     Age >= 4 & Age <= 6 ~ (Avg_Magnesiummg/120)*100,
                                     Age >= 7 & Age <= 10 ~ (Avg_Magnesiummg/200)*100,
                                     Age >= 11 & Age <= 14 ~ (Avg_Magnesiummg/280)*100,
                                     Age >= 15 & Age <= 18 ~ (Avg_Magnesiummg/300)*100,
      
                                     TRUE ~ NA_integer_)
           ) %>% 
  
    relocate(RNI_Magnesium, LRNI_Magnesium, RNI_prct_Magnesium, .after = Avg_Magnesiummg)

# potassium - no differences between males and females
df.intake24_participant <- df.intake24_participant %>%  
    mutate(RNI_Potassium = case_when(Age >= 1 & Age <= 3 & Avg_Potassiummg >= 800 ~ 0,
                                     Age >= 4 & Age <= 6 & Avg_Potassiummg >= 1100 ~ 0,
                                     Age >= 7 & Age <= 10 & Avg_Potassiummg >= 2000 ~ 0,
                                     Age >= 11 & Age <= 14 & Avg_Potassiummg >= 3100 ~ 0,
                                     Age >= 15 & Age <= 18 & Avg_Potassiummg >= 3500 ~ 0,
                                      
                                     Age >= 1 & Age <= 3 & Avg_Potassiummg < 800 ~ 1,
                                     Age >= 4 & Age <= 6 & Avg_Potassiummg < 1100 ~ 1,
                                     Age >= 7 & Age <= 10 & Avg_Potassiummg < 2000 ~ 1,
                                     Age >= 11 & Age <= 14 & Avg_Potassiummg < 3100 ~ 1,
                                     Age >= 15 & Age <= 18 & Avg_Potassiummg < 3500 ~ 1,
                                      
                                     TRUE ~ NA_integer_),
           
           LRNI_Potassium = case_when(Age >= 1 & Age <= 3 & Avg_Potassiummg >= 450 ~ 0, 
                                      Age >= 4 & Age <= 6 & Avg_Potassiummg >= 600 ~ 0,
                                      Age >= 7 & Age <= 10 & Avg_Potassiummg >= 950 ~ 0,
                                      Age >= 11 & Age <= 14 & Avg_Potassiummg >= 1600 ~ 0,
                                      Age >= 15 & Age <=18 & Avg_Potassiummg >= 2000 ~ 0,
                                       
                                      Age >= 1 & Age <= 3 & Avg_Potassiummg < 450 ~ 1,
                                      Age >= 4 & Age <= 6 & Avg_Potassiummg < 600 ~ 1,
                                      Age >= 7 & Age <= 10 & Avg_Potassiummg < 950 ~ 1,
                                      Age >= 11 & Age <= 14 & Avg_Potassiummg < 1600 ~ 1,
                                      Age >= 15 & Age <=18 & Avg_Potassiummg < 2000 ~ 1,
                                       
                                      TRUE ~ NA_integer_),
                     
      RNI_prct_Potassium = case_when(Age >= 1 & Age <= 3 ~ (Avg_Potassiummg/800)*100,
                                     Age >= 4 & Age <= 6 ~ (Avg_Potassiummg/1100)*100,
                                     Age >= 7 & Age <= 10 ~ (Avg_Potassiummg/2000)*100,
                                     Age >= 11 & Age <= 14 ~ (Avg_Potassiummg/3100)*100,
                                     Age >= 15 & Age <= 18 ~ (Avg_Potassiummg/3500)*100,
      
                                     TRUE ~ NA_integer_)
           ) %>% 
  
    relocate(RNI_Potassium, LRNI_Potassium, RNI_prct_Potassium, .after = Avg_Potassiummg)

# iodine - no differences between males and females
df.intake24_participant <- df.intake24_participant %>%  
    mutate(RNI_Iodine = case_when(Age >= 1 & Age <= 3 & Avg_Iodineug >= 70 ~ 0,
                                     Age >= 4 & Age <= 6 & Avg_Iodineug >= 100 ~ 0,
                                     Age >= 7 & Age <= 10 & Avg_Iodineug >= 110 ~ 0,
                                     Age >= 11 & Age <= 14 & Avg_Iodineug >= 130 ~ 0,
                                     Age >= 15 & Age <= 18 & Avg_Iodineug >= 140 ~ 0,
                                      
                                     Age >= 1 & Age <= 3 & Avg_Iodineug < 70 ~ 1,
                                     Age >= 4 & Age <= 6 & Avg_Iodineug < 100 ~ 1,
                                     Age >= 7 & Age <= 10 & Avg_Iodineug < 110 ~ 1,
                                     Age >= 11 & Age <= 14 & Avg_Iodineug < 130 ~ 1,
                                     Age >= 15 & Age <= 18 & Avg_Iodineug < 140 ~ 1,
                                      
                                     TRUE ~ NA_integer_),
           
           LRNI_Iodine = case_when(Age >= 1 & Age <= 3 & Avg_Iodineug >= 40 ~ 0, 
                                      Age >= 4 & Age <= 6 & Avg_Iodineug >= 50 ~ 0,
                                      Age >= 7 & Age <= 10 & Avg_Iodineug >= 55 ~ 0,
                                      Age >= 11 & Age <= 14 & Avg_Iodineug >= 65 ~ 0,
                                      Age >= 15 & Age <=18 & Avg_Iodineug >= 70 ~ 0,
                                       
                                      Age >= 1 & Age <= 3 & Avg_Iodineug < 40 ~ 1,
                                      Age >= 4 & Age <= 6 & Avg_Iodineug < 50 ~ 1,
                                      Age >= 7 & Age <= 10 & Avg_Iodineug < 55 ~ 1,
                                      Age >= 11 & Age <= 14 & Avg_Iodineug < 65 ~ 1,
                                      Age >= 15 & Age <=18 & Avg_Iodineug < 70 ~ 1,
                                       
                                      TRUE ~ NA_integer_),
                     
      RNI_prct_Iodine = case_when(Age >= 1 & Age <= 3 ~ (Avg_Iodineug/85)*70,
                                     Age >= 4 & Age <= 6 ~ (Avg_Iodineug/100)*100,
                                     Age >= 7 & Age <= 10 ~ (Avg_Iodineug/110)*100,
                                     Age >= 11 & Age <= 14 ~ (Avg_Iodineug/130)*100,
                                     Age >= 15 & Age <= 18 ~ (Avg_Iodineug/140)*100,
      
                                     TRUE ~ NA_integer_)
           ) %>% 
  
    relocate(RNI_Iodine, LRNI_Iodine, RNI_prct_Iodine, .after = Avg_Iodineug)

# selenium 
df.intake24_participant <- df.intake24_participant %>%
    mutate(RNI_Selenium = case_when(Age >= 1 & Age <= 3 & Avg_Seleniumug >= 15 ~ 0,
                                    Age >= 4 & Age <= 6 & Avg_Seleniumug >=20 ~ 0,
                                    Age >= 7 & Age <= 10 & Avg_Seleniumug >= 30 ~ 0,
                                    Age >= 11 & Age <= 14 & Avg_Seleniumug >= 45 ~ 0,
                                    Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Seleniumug >= 70 ~ 0,
                                    Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Seleniumug >= 60 ~ 0,
                                    
                                    Age >= 1 & Age <= 3 & Avg_Seleniumug < 15 ~ 1,
                                    Age >= 4 & Age <= 6 & Avg_Seleniumug < 20 ~ 1,
                                    Age >= 7 & Age <= 10 & Avg_Seleniumug < 30 ~ 1,
                                    Age >= 11 & Age <= 14 & Avg_Seleniumug < 45 ~ 1,
                                    Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Seleniumug < 70 ~ 1,
                                    Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Seleniumug < 60 ~ 1,
           
                                    TRUE ~ NA_integer_),
           
           LRNI_Selenium = case_when(Age >= 1 & Age <= 3 & Avg_Seleniumug >= 7 ~ 0,
                                     Age >= 4 & Age <= 6 & Avg_Seleniumug >= 10 ~ 0,
                                     Age >= 7 & Age <= 10 & Avg_Seleniumug >= 16 ~ 0,
                                     Age >= 11 & Age <= 14 & Avg_Seleniumug >= 25 ~ 0,
                                     Age >= 15 & Age <= 18 & Avg_Seleniumug >= 40 ~ 0,
                                     
                                    Age >= 1 & Age <= 3 & Avg_Seleniumug < 7 ~ 1,
                                    Age >= 4 & Age <= 6 & Avg_Seleniumug < 10 ~ 1,
                                    Age >= 7 & Age <= 10 & Avg_Seleniumug < 16 ~ 1,
                                    Age >= 11 & Age <= 14 & Avg_Seleniumug < 25 ~ 1,
                                    Age >= 15 & Age <= 18 & Avg_Seleniumug < 40 ~ 1,
                                   
                                    TRUE ~ NA_integer_),
                     
      RNI_prct_Selenium = case_when(Age >= 1 & Age <= 3 ~ (Avg_Seleniumug/15)*70,
                                    Age >= 4 & Age <= 6 ~ (Avg_Seleniumug/20)*100,
                                    Age >= 7 & Age <= 10 ~ (Avg_Seleniumug/30)*100,
                                    Age >= 11 & Age <= 14 ~ (Avg_Seleniumug/45)*100,
                                    Sex == "Male" & Age >= 15 & Age <= 18 ~ (Avg_Seleniumug/70)*100,
                                    Sex == "Female" & Age >= 15 & Age <= 18 ~ (Avg_Seleniumug/60)*100,
      
                                     TRUE ~ NA_integer_)
           ) %>% 
  
    relocate(RNI_Selenium, LRNI_Selenium, RNI_prct_Selenium, .after = Avg_Seleniumug)

# zinc   
df.intake24_participant <- df.intake24_participant %>%
    mutate(RNI_Zinc = case_when(Age >= 1 & Age <= 3 & Avg_Zincmg >= 5.0 ~ 0,
                                Age >= 4 & Age <= 6 & Avg_Zincmg >= 6.5 ~ 0,
                                Age >= 7 & Age <= 10 & Avg_Zincmg >= 7.0 ~ 0,
                                Age >= 11 & Age <= 14 & Avg_Zincmg >= 9.0 ~ 0,
                                Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Zincmg >= 9.5 ~ 0,
                                Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Zincmg >= 7.0 ~ 0,
                                
                                Age >= 1 & Age <= 3 & Avg_Zincmg < 5.0 ~ 1,
                                Age >= 4 & Age <= 6 & Avg_Zincmg < 6.5 ~ 1,
                                Age >= 7 & Age <= 10 & Avg_Zincmg < 7.0 ~ 1,
                                Age >= 11 & Age <= 14 & Avg_Zincmg < 9.0 ~ 1,
                                Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Zincmg < 9.5 ~ 1,
                                Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Zincmg < 7.0 ~ 1,
           
                                TRUE ~ NA_integer_),
           
           LRNI_Zinc = case_when(Age >= 1 & Age <= 3 & Avg_Zincmg >= 3.0 ~ 0, 
                                 Age >= 4 & Age <= 6 & Avg_Zincmg >= 4.0 ~ 0,
                                 Age >= 7 & Age <= 10 & Avg_Zincmg >= 4.0 ~ 0,
                                 Age >= 11 & Age <= 14 & Avg_Zincmg >= 5.3 ~ 0,
                                 Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Zincmg >= 5.5 ~ 0,
                                 Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Zincmg >= 4.0 ~ 0,
                                 
                                 Age >= 1 & Age < 4 & Avg_Zincmg < 3.0 ~ 1,
                                   Age >= 4 & Age < 7 & Avg_Zincmg < 4.0 ~ 1,
                                   Age >= 7 & Age < 11 & Avg_Zincmg < 4.0 ~ 1,
                                   Age >= 11 & Age < 15 & Avg_Zincmg < 5.3 ~ 1,
                                   Sex == "Male" & Age >= 15 & Age <= 18 & Avg_Zincmg < 5.5 ~ 1,
                                   Sex == "Female" & Age >= 15 & Age <= 18 & Avg_Zincmg < 4.0 ~ 1,
                                 
                                   TRUE ~ NA_integer_),
                     
      RNI_prct_Zinc = case_when(Age >= 1 & Age <= 3 ~ (Avg_Zincmg/5.0)*70,
                                Age >= 4 & Age <= 6 ~ (Avg_Zincmg/6.5)*100,
                                Age >= 7 & Age <= 10 ~ (Avg_Zincmg/7.0)*100,
                                Age >= 11 & Age <= 14 ~ (Avg_Zincmg/9.0)*100,
                                Sex == "Male" & Age >= 15 & Age <= 18 ~ (Avg_Zincmg/9.5)*100,
                                Sex == "Female" & Age >= 15 & Age <= 18 ~ (Avg_Zincmg/7.0)*100,
      
                                TRUE ~ NA_integer_)
           ) %>% 
  
    relocate(RNI_Zinc, LRNI_Zinc, RNI_prct_Zinc, .after = Avg_Zincmg)

## Add values "Below" or "Above"
df.intake24_participant <- df.intake24_participant %>%
  mutate(across(c(RNI_VitaminA, LRNI_VitaminA, RNI_Riboflavin, LRNI_Riboflavin, RNI_Folate, LRNI_Folate, RNI_VitaminD, RNI_VitaminB12, LRNI_VitaminB12, RNI_VitaminC, LRNI_VitaminC, RNI_Iron, LRNI_Iron, RNI_Calcium, LRNI_Calcium, RNI_Magnesium, LRNI_Magnesium, RNI_Potassium, LRNI_Potassium, RNI_Iodine, LRNI_Iodine, RNI_Selenium, LRNI_Selenium, RNI_Zinc, LRNI_Zinc),as.factor))

df.intake24_participant <- df.intake24_participant %>%
  mutate(RNI_VitaminA=fct_recode(RNI_VitaminA,"Below"="1", "Above"="0"),
         LRNI_VitaminA=fct_recode(LRNI_VitaminA,"Below"="1", "Above"="0"),
         RNI_Riboflavin=fct_recode(RNI_Riboflavin,"Below"="1", "Above"="0"),
         LRNI_Riboflavin=fct_recode(LRNI_Riboflavin,"Below"="1", "Above"="0"),
         RNI_Folate=fct_recode(RNI_Folate,"Below"="1", "Above"="0"),
         LRNI_Folate=fct_recode(LRNI_Folate,"Below"="1", "Above"="0"),
         RNI_VitaminD=fct_recode(RNI_VitaminD,"Below"="1", "Above"="0"),
         RNI_VitaminB12=fct_recode(RNI_VitaminB12,"Below"="1", "Above"="0"),
         LRNI_VitaminB12=fct_recode(LRNI_VitaminB12,"Below"="1", "Above"="0"),
         RNI_VitaminC=fct_recode(RNI_VitaminC,"Below"="1", "Above"="0"),
         LRNI_VitaminC=fct_recode(LRNI_VitaminC,"Below"="1", "Above"="0"),
         RNI_Iron=fct_recode(RNI_Iron,"Below"="1", "Above"="0"),
         LRNI_Iron=fct_recode(LRNI_Iron,"Below"="1", "Above"="0"),
         RNI_Calcium=fct_recode(RNI_Calcium,"Below"="1", "Above"="0"),
         LRNI_Calcium=fct_recode(LRNI_Calcium,"Below"="1", "Above"="0"),
         RNI_Magnesium=fct_recode(RNI_Magnesium,"Below"="1", "Above"="0"),
         LRNI_Magnesium=fct_recode(LRNI_Magnesium,"Below"="1", "Above"="0"),
         RNI_Potassium=fct_recode(RNI_Potassium,"Below"="1", "Above"="0"),
         LRNI_Potassium=fct_recode(LRNI_Potassium,"Below"="1", "Above"="0"),
         RNI_Iodine=fct_recode(RNI_Iodine,"Below"="1", "Above"="0"),
         LRNI_Iodine=fct_recode(LRNI_Iodine,"Below"="1", "Above"="0"),
         RNI_Selenium=fct_recode(RNI_Selenium,"Below"="1", "Above"="0"),
         LRNI_Selenium=fct_recode(LRNI_Selenium,"Below"="1", "Above"="0"),
         RNI_Zinc=fct_recode(RNI_Zinc,"Below"="1", "Above"="0"),
         LRNI_Zinc=fct_recode(LRNI_Zinc,"Below"="1", "Above"="0"))
```

# Write files for analysis
```{r include=FALSE}
#write.csv(df.intake24_participant, file = "/Users/ricki/Desktop/DISH_data_cleaning/Output_data_analysis/intake24_participant_060924.csv")
#write.csv(df.intake24_recall, file = "/Users/ricki/Desktop/DISH_data_cleaning/Output_data_analysis/intake24_recall_060924.csv")
#write.csv(df.intake24_item, file = "/Users/ricki/Desktop/DISH_data_cleaning/Output_data_analysis/intake24_item_060924.csv")
#write.csv(df.intake24_participant_ndns_fg, file = "/Users/ricki/Desktop/DISH_data_cleaning/Output_data_analysis/intake24_ndns_food_groups_060924.csv")
#write.csv(df.intake24_participant_fg, file = "/Users/ricki/Desktop/DISH_data_cleaning/Output_data_analysis/intake24_reporting_food_groups_060924.csv")



write.csv(df.intake24_participant, file = "C:/Users/ljaacks/OneDrive - University of Edinburgh/Scottish Diets/_National Monitoring of Diet Scotland/3_DISH/Analysis/Data/intake24_participant_280824.csv")
write.csv(df.intake24_recall, file = "C:/Users/ljaacks/OneDrive - University of Edinburgh/Scottish Diets/_National Monitoring of Diet Scotland/3_DISH/Analysis/Data/intake24_recall_280824.csv")
write.csv(df.intake24_item, file = "C:/Users/ljaacks/OneDrive - University of Edinburgh/Scottish Diets/_National Monitoring of Diet Scotland/3_DISH/Analysis/Data/intake24_item_280824.csv")

#New food group files

#NDNS food groups
write.csv(df.intake24_participant_ndns_fg, file = "C:/Users/ljaacks/OneDrive - University of Edinburgh/Scottish Diets/_National Monitoring of Diet Scotland/3_DISH/Analysis/Data/intake24_ndns_food_groups_060924.csv")

#Reporting/Discretionary food groups
write.csv(df.intake24_participant_fg, file = "C:/Users/ljaacks/OneDrive - University of Edinburgh/Scottish Diets/_National Monitoring of Diet Scotland/3_DISH/Analysis/Data/intake24_reporting_food_groups_060924.csv")

```
