---
title: "DISH_Prelim_Results"
output:
  word_document: default
  html_notebook: default
---


# Prepare R Environment 
```{r include=FALSE}

  # Clear R environment
  rm(list = ls())
  
  # Load required packages
  library(dplyr)
  library(tidyr)
  library(rio)
  library(ggplot2)
  library(ggthemes)
  library(grafify)
  library(lubridate)
  library(stringr)
  library(XLConnect)
  library(flextable)
  library(gtsummary)
  library(writexl)
  library(forcats)
  library(purrr)
```

#Import the data
```{r include=FALSE}
  
  df.intake24_participant <- read.csv("/Users/ricki/Desktop/DISH_data_cleaning/Output_data_analysis/intake24_participant_foodgroups_SDG_RNI_LRNI_20_08_24.csv") %>%
    select(-X)
  
 # df.intake24_participant_fg <- read.csv("/Users/ricki/Desktop/DISH_data_cleaning/Output_data_analysis/recall_foodgroups_SDG_RNI_15_07_24.csv") %>%
    #select(-X)
  
  df.intake24_item <- read.csv( "/Users/ricki/Desktop/DISH_data_cleaning/Output_data_analysis/intake24_item_20_08_24.csv") %>%
    select(-X)

  df.intake24_recall <- read.csv("/Users/ricki/Desktop/DISH_data_cleaning/Output_data_analysis/intake24_recall_20_08_24.csv") %>%
  select(-X)

  df.survey <- read.csv( "/Users/ricki/Desktop/DISH_data_cleaning/Output/survey_clean_for_management_200824.csv") %>%
    select(-X)
  
  user_char <- read.csv("/Users/ricki/Desktop/DISH_data_cleaning/Output/user_characteristics.csv") %>%
    select(-X)
```







```{r include=FALSE}
meat <- df.intake24_participant %>%
  select(UserID, Avg_redmeat, Avg_processedmeat, Avg_redprocessedmeat)

meat_ffq <- df.survey %>%
  select(UserID, AFreqRRPM, YPFreqRRPM)


meat_g_ffq <- left_join(meat, meat_ffq, by = "UserID")

meat_g_ffq <- left_join(meat_g_ffq, user_char, by = "UserID")


```

We are only comparing Avg_redprocessedmeat to FFQ because the FFQ question asks about red and red processed meat together, so it is the only comparable disag variable. 
```{r include=FALSE}
meat_g_ffq$AFreqRRPM <- factor(meat_g_ffq$AFreqRRPM, levels = c("Every day", "4-6 times a week", "2-3 times a week", "Once a week", "Less than once a week", "Never", "Not sure"))

meat_g_ffq$AFreqRRPM <- fct_explicit_na(meat_g_ffq$AFreqRRPM)   

meat_g_ffq %>% 
  select(Avg_redprocessedmeat, AFreqRRPM) %>%
  tbl_summary(missing = "no",
              digits = list(all_categorical() ~ c(1,0)),
              type = list(all_continuous() ~ "continuous2"),
              statistic = list(all_continuous() ~ c("{median}",
                                                   "{mean} ({sd})",
                                                    "{min}, {max}")),
              by = AFreqRRPM
  ) %>%
  add_overall() %>%
  modify_header(label ~ "****") %>%
  bold_labels() %>%  
  as_flex_table()
```

The zero here is due to rounding in the table, there is one respondent who ate 0.31 grams once a week
```{r include=FALSE}
meat_g_ffq %>% 
  filter(Avg_redprocessedmeat != 0) %>%
  select(Avg_redprocessedmeat, AFreqRRPM) %>%
  tbl_summary(missing = "no",
              digits = list(all_categorical() ~ c(1,0)),
              type = list(all_continuous() ~ "continuous2"),
              statistic = list(all_continuous() ~ c("{median}",
                                                   "{mean} ({sd})",
                                                    "{min}, {max}")),
              by = AFreqRRPM
  ) %>%
  add_overall() %>%
  modify_header(label ~ "****") %>%
  bold_labels() %>%  
  as_flex_table()
```

```{r eval=FALSE, include=FALSE}
check <- meat_g_ffq %>%
  filter(Avg_redprocessedmeat != 0) %>%
  filter(AFreqRRPM == "Once a week")


```

```{r eval=FALSE, include=FALSE}

check <- meat_g_ffq %>%
  filter(AFreqRRPM == "(Missing)")

```


#RNI and LRNI Tables***
Results are presented for 
1. Average Daily Intakes overall
2. Average Daily Intakes by Sex
3. SDG Results
3. Adherence to RNIs overall and by age group
4. Adherence to RNIs by age and sex
5. Adherence to LRNIs by age and sex


Set factors and remove na
```{r include=FALSE}
df.intake24_participant$age_cat <- factor(df.intake24_participant$age_cat, levels = c("2-4y", "5-10y", "11-15y"))

df.intake24_participant %>%
  filter(is.na(df.intake24_participant$age_cat))
```

Set factors
```{r include=FALSE}
# set variables as factors for gtsummary

# RNI factors
df.intake24_participant$Sex <- factor(df.intake24_participant$Sex)
df.intake24_participant$VitaminB12RNI <- as.factor(df.intake24_participant$VitaminB12RNI)
df.intake24_participant$ZincRNI <- as.factor(df.intake24_participant$ZincRNI)
df.intake24_participant$SeleniumRNI <- as.factor(df.intake24_participant$SeleniumRNI)
df.intake24_participant$IronRNI <- as.factor(df.intake24_participant$IronRNI)
df.intake24_participant$ProteinRNI <- as.factor(df.intake24_participant$ProteinRNI)
df.intake24_participant$CalciumRNI <- as.factor(df.intake24_participant$CalciumRNI)
df.intake24_participant$age_cat <- factor(df.intake24_participant$age_cat)

# LRNI factors
df.intake24_participant$VitaminB12LRNI <- as.factor(df.intake24_participant$VitaminB12LRNI)
df.intake24_participant$ZincLRNI <- factor(df.intake24_participant$ZincLRNI)
df.intake24_participant$SeleniumLRNI <- as.factor(df.intake24_participant$SeleniumLRNI)
df.intake24_participant$IronLRNI <- factor(df.intake24_participant$IronLRNI)
df.intake24_participant$CalciumLRNI <- factor(df.intake24_participant$CalciumLRNI)

```

Create full-demo subset
```{r include=FALSE}
# create a subset that removes any participant without full demographic information (age/sex variables)
df.intake24_full_demo <- df.intake24_participant %>% 
  filter(Sex != "Prefer not to say")

# set factor level
df.intake24_full_demo$Sex <- factor(df.intake24_full_demo$Sex, levels = c("Female", "Male"))
```

##***Daily Intakes***
##Overall
```{r echo=FALSE}
df.intake24_participant %>% 
  select(Avg_EnergyDensity, Avg_Portions_Total, Avg_redprocessedmeat, Avg_Fat_PropFoodEnergy, Avg_SatFat_PropFoodEnergy, Avg_TransFat_PropFoodEnergy, Avg_TotalSugars_PropFoodEnergy, Avg_Carbs_PropFoodEnergy, Avg_AOACFibre) %>% # select variables for table
  tbl_summary(missing = "no", # set to 'always' or 'ifany' to show unknowns in table
              digits = list(all_categorical() ~ c(1,0)), # set categorical variables to one decimal place
              type = list(all_continuous() ~ "continuous2"), 
              statistic = list(all_continuous() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})")),
              label = c(        # rename variables for table               
                Avg_EnergyDensity ~ "Energy density",
                Avg_Portions_Total ~ "Fruit and vegetables - portions/day",
                Avg_redprocessedmeat ~ "Red and red processed meat - g/day",
                Avg_Fat_PropFoodEnergy ~ "Total fat - % food energy",
                Avg_SatFat_PropFoodEnergy ~ "Saturated fat - % food energy",
                Avg_TransFat_PropFoodEnergy ~ "Trans fat - % food energy",
                Avg_TotalSugars_PropFoodEnergy ~ "Free sugars - % food energy",
                Avg_Carbs_PropFoodEnergy ~ "Total carbs - % food energy",
                Avg_AOACFibre ~ "Fibre - g/day"
                )
  ) %>%
  add_ci() %>% #add confidence interval
  modify_header(label ~ "**Mean Daily Intakes**") %>% #change header 
  bold_labels() %>%
  as_flex_table()
```


```{r}
# set up stats
stats <- c("N" = "{length}", 
           "Mean (SD)" = "{mean} ({sd})", 
           "Median (IQR)" = "{median} ({p25}, {p75})")


df.intakes <- df.intake24_participant %>% 
  select(Avg_EnergyDensity, Avg_Portions_Total, Avg_redprocessedmeat, Avg_Fat_PropFoodEnergy, Avg_SatFat_PropFoodEnergy, Avg_TransFat_PropFoodEnergy, Avg_TotalSugars_PropFoodEnergy, Avg_Carbs_PropFoodEnergy, Avg_AOACFibre) # select variables for table

#useimap from purr package to combine summary tables and reformat with stats in header row
intakes_reformat <- imap( 
    stats,
    ~ df.intakes %>%
  tbl_summary(missing = "no", # set to 'always' or 'ifany' to show unknowns in table
              statistic = ~.x,
              label = c(        # rename variables for table               
                Avg_EnergyDensity ~ "Energy density",
                Avg_Portions_Total ~ "Fruit and vegetables - portions/day",
                Avg_redprocessedmeat ~ "Red and red processed meat - g/day",
                Avg_Fat_PropFoodEnergy ~ "Total fat - % food energy",
                Avg_SatFat_PropFoodEnergy ~ "Saturated fat - % food energy",
                Avg_TransFat_PropFoodEnergy ~ "Trans fat - % food energy",
                Avg_TotalSugars_PropFoodEnergy ~ "Free sugars - % food energy",
                Avg_Carbs_PropFoodEnergy ~ "Total carbs - % food energy",
                Avg_AOACFibre ~ "Fibre - g/day"
                )) %>%

    modify_header(all_stat_cols() ~ stringr::str_glue("**{.y}**"))
  ) %>%
  # Merge the individual summary tables into one table
  tbl_merge(tab_spanner = FALSE) %>%
  modify_header(label ~ "**Mean Daily Intakes**") %>% #change header 
  bold_labels() %>%
  as_flex_table()
  
intakes_reformat

```

```{r eval=FALSE, include=FALSE}
##ME TRYING TO FIGURE OUT OTHER FORMATS

df.intakes %>%
  tbl_summary(),

 # set to 'always' or 'ifany' to show unknowns in table
             digits = list(all_categorical() ~ c(1,0)), # set categorical variables to one decimal place
              type = list(all_continuous() ~ "continuous2"), 
              statistic = list(all_continuous() ~ c("{mean} ({sd})")),
              label = c(        # rename variables for table               
                Avg_EnergyDensity ~ "Energy density",
                Avg_Portions_Total ~ "Fruit and vegetables - portions/day",
                Avg_redprocessedmeat ~ "Red and red processed meat - g/day",
                Avg_Fat_PropFoodEnergy ~ "Total fat - % food energy",
                Avg_SatFat_PropFoodEnergy ~ "Saturated fat - % food energy",
                Avg_TransFat_PropFoodEnergy ~ "Trans fat - % food energy",
                Avg_TotalSugars_PropFoodEnergy ~ "Free sugars - % food energy",
                Avg_Carbs_PropFoodEnergy ~ "Total carbs - % food energy",
                Avg_AOACFibre ~ "Fibre - g/day"
                )
```

##Daily Intakes by Age
*13 participants removed that refused demographic information
```{r echo=FALSE}

df.intake24_full_demo %>% 
  select(age_cat, Avg_EnergyDensity, Avg_Portions_FruitSmoothie, Avg_redprocessedmeat, Avg_Fat_PropFoodEnergy, Avg_SatFat_PropFoodEnergy, Avg_TransFat_PropFoodEnergy, Avg_TotalSugars_PropFoodEnergy, Avg_Carbs_PropFoodEnergy, Avg_AOACFibre) %>%
  tbl_summary(missing = "no",
              digits = list(all_categorical() ~ c(1,0)),
              type = list(all_continuous() ~ "continuous2"),
              statistic = list(all_continuous() ~ c("{mean} ({sd})",
                                                    "{median} ({p25}, {p75})")),
              by = age_cat, 
              label = c(
                Avg_EnergyDensity ~ "Energy density",
                Avg_Portions_FruitSmoothie ~ "Fruit and vegetables - portions/day",
                Avg_redprocessedmeat ~ "Red and red processed meat - g/day",
                Avg_Fat_PropFoodEnergy ~ "Total fat - % food energy",
                Avg_SatFat_PropFoodEnergy ~ "Saturated fat - % food energy",
                Avg_TransFat_PropFoodEnergy ~ "Trans fat - % food energy",
                Avg_TotalSugars_PropFoodEnergy ~ "Free sugars - % food energy",
                Avg_Carbs_PropFoodEnergy ~ "Total carbs - % food energy",
                Avg_AOACFibre ~ "Fibre - g/day"
                )
  ) %>%
  add_p() %>%
  add_significance_stars() %>%
  modify_header(label ~ "**Daily Intakes**") %>%
  bold_labels() %>%  
  as_flex_table() 
```

##Daily Intakes by Sex
*13 participants removed that refused demographic information
```{r echo=FALSE}

df.intake24_full_demo %>% 
  select(Sex, Avg_EnergyDensity, Avg_Portions_FruitSmoothie, Avg_redprocessedmeat, Avg_Fat_PropFoodEnergy, Avg_SatFat_PropFoodEnergy, Avg_TransFat_PropFoodEnergy, Avg_TotalSugars_PropFoodEnergy, Avg_Carbs_PropFoodEnergy, Avg_AOACFibre) %>%
  tbl_summary(missing = "no",
              digits = list(all_categorical() ~ c(1,0)),
              type = list(all_continuous() ~ "continuous2"),
              statistic = list(all_continuous() ~ c("{mean} ({sd})",
                                                    "{median} ({p25}, {p75})")),
              by = Sex, 
              label = c(
                Avg_EnergyDensity ~ "Energy density",
                Avg_Portions_FruitSmoothie ~ "Fruit and vegetables - portions/day",
                Avg_redprocessedmeat ~ "Red and red processed meat - g/day",
                Avg_Fat_PropFoodEnergy ~ "Total fat - % food energy",
                Avg_SatFat_PropFoodEnergy ~ "Saturated fat - % food energy",
                Avg_TransFat_PropFoodEnergy ~ "Trans fat - % food energy",
                Avg_TotalSugars_PropFoodEnergy ~ "Free sugars - % food energy",
                Avg_Carbs_PropFoodEnergy ~ "Total carbs - % food energy",
                Avg_AOACFibre ~ "Fibre - g/day"
                )
  ) %>%
  add_p() %>%
  add_significance_stars() %>%
  modify_header(label ~ "**Daily Intakes**") %>%
  bold_labels() %>%  
  as_flex_table() 
```


##SDG Results
###Intake24 
```{r echo=FALSE}
#set factor levels and make NA a level
    df.intake24_participant$age_cat <- factor(df.intake24_participant$age_cat, levels = c("2-4y", "5-10y", "11-15y"))
    df.intake24_participant$age_cat <- fct_explicit_na(df.intake24_participant$age_cat)
    
    df.intake24_participant %>% 
      select(age_cat, SDG_Energy, SDG_Fat, SDG_SatFat, SDG_TransFat, SDG_Sugar, SDG_Carbs, SDG_Fibre, SDG_Salt, SDG_FV, SDG_FV_NoFruitSmoothie, SDG_RRPM, SDG_oilyfish) %>% 
      tbl_summary(missing = "no",
                  digits = list(all_categorical() ~ c(1,0)),
                  type = list(all_continuous() ~ "continuous2"),
                  statistic = list(all_continuous() ~ c("{mean} ({sd})",
                                                        "{min}, {max}")),
                  by = age_cat,
                  label = c(SDG_Energy ~ "Energy density",
                            SDG_Fat ~ "Total fat",
                            SDG_SatFat ~ "Saturated fat",
                            SDG_TransFat ~ "Trans fat",
                            SDG_Sugar ~ "Total sugar",
                            SDG_Carbs ~ "Carbohydrates",
                            SDG_Fibre ~ "Fibre",
                            SDG_Salt ~ "Salt",
                            SDG_FV ~ "Fruit and vegetables - portion/day",
                            SDG_FV_NoFruitSmoothie ~ "Fruit and vegetables - no fruit smoothie - portion/day",
                            SDG_RRPM ~ "Red and red processed meat",
                            SDG_oilyfish ~ "Oily fish"
                    
                  )
      ) %>%
      add_overall() %>%
      modify_header(label ~ "**SDG **") %>%
      bold_labels() %>%  
      as_flex_table()
```

###Oily Fish FFQ
```{r echo=FALSE}
df.survey$age_cat <- factor(df.survey$age_cat, levels = c("2-4y", "5-10y", "11-15y"))
    df.survey$age_cat <- fct_explicit_na(df.survey$age_cat)    
    
    
df.survey$AFreqRRPM <- factor(df.survey$AFreqRRPM, levels = c("Every day", "4-6 times a week", "2-3 times a week", "Once a week", "Less than once a week", "Never", "Not sure" ))
df.survey$AFreqRRPM <- fct_explicit_na(df.survey$AFreqRRPM)

df.survey$AFreqOilyFish <- factor(df.survey$AFreqOilyFish, levels = c("Every day", "4-6 times a week", "2-3 times a week", "Once a week", "Less than once a week", "Never", "Not sure" ))
df.survey$AFreqOilyFish <- fct_explicit_na(df.survey$AFreqOilyFish)

df.survey %>% 
  select(age_cat, AFreqOilyFish) %>%
  tbl_summary(missing = "no",
              digits = list(all_categorical() ~ c(1,0)),
              type = list(all_continuous() ~ "continuous2"),
              statistic = list(all_continuous() ~ c("{mean} ({sd})",
                                                    "{min}, {max}")),
              by = age_cat,
              label = AFreqOilyFish ~ "Oily Fish"
  ) %>%
  add_overall() %>%
  modify_header(label ~ "**SDG **") %>%
  bold_labels() %>%  
  as_flex_table()
```

##RNIs and LRNIs

###RNI overall and by age
*13 participants removed that refused demographic information. Not included in report as we are only reported by age/sex.
```{r include=FALSE}
df.intake24_full_demo %>% 
  select(age_cat, ProteinRNI, CalciumRNI, IronRNI, SeleniumRNI, ZincRNI, VitaminB12RNI) %>%
  tbl_summary(missing = "no",
              digits = list(all_categorical() ~ c(1,0)),
              type = list(all_continuous() ~ "continuous2"),
              statistic = list(all_continuous() ~ c("{mean} ({sd})",
                                                    "{min}, {max}")),
              by = age_cat
  ) %>%
  add_p()%>%
  add_significance_stars() %>%
  add_overall() %>%
  modify_header(label ~ "**RNI**") %>%
  bold_labels() %>%  
  as_flex_table()


```


###RNI by age and sex
*13 participants removed that refused demographic information
```{r echo=FALSE}

df.intake24_full_demo %>% 
  select(Sex, age_cat, ProteinRNI, CalciumRNI, IronRNI, SeleniumRNI, ZincRNI, VitaminB12RNI) %>%
  tbl_strata(strata = Sex,
             .tbl_fun = ~.x %>%
               tbl_summary(missing = "no",
               by = age_cat,
               label = c(ProteinRNI ~ "Protein",
                         CalciumRNI ~ "Calcium",
                         IronRNI ~ "Iron",
                         SeleniumRNI ~ "Selenium",
                         ZincRNI ~ "Zinc",
                         VitaminB12RNI ~ "Vitamin B12"
                         ))
  ) %>%
  modify_header(label ~ "**RNI**") %>%
  bold_labels() %>%  
  as_flex_table()

```

###LRNI by age and sex
*13 participants removed that refused demographic information
```{r echo=FALSE}

df.intake24_full_demo %>% 
  select(Sex, age_cat, CalciumLRNI, IronLRNI, SeleniumLRNI, ZincLRNI, VitaminB12LRNI) %>%
  tbl_strata(strata = Sex,
             .tbl_fun = ~.x %>%
               tbl_summary(missing = "no",
               by = age_cat,
               label = c(
                         CalciumLRNI ~ "Calcium",
                         IronLRNI ~ "Iron",
                         SeleniumLRNI ~ "Selenium",
                         ZincLRNI ~ "Zinc",
                         VitaminB12LRNI ~ "Vitamin B12"
                         ))
  ) %>%
  modify_header(label ~ "**LRNI**") %>%
  bold_labels() %>%  
  as_flex_table()
```

#Most Commonly Reported Vegetables
```{r include=FALSE}
Vegetables <- df.intake24_item %>%
  filter(MainFoodGroupCode %in% c(37, 36))

Veg_sub <- Vegetables %>%
  select(UserID, SearchTerm, Description_English, Description_Local, FoodGroupCode, FoodGroupEnglish, ReadyMeal, RecallNo, NumberOfRecalls, NumberOfItems, Sex, CalcAge, simd_quintile, age_cat, NewMealName, MainFoodGroupCode, MainFoodGroupDesc, ReportingFoodGroupCode, ReportingFoodGroupDesc)

Veg_sub$age_cat <- factor(Veg_sub$age_cat, levels = c("2-4y", "5-10y", "11-15y"))
```


```{r echo=FALSE}
Veg_sub %>%
  filter(ReportingFoodGroupCode == 5) %>%
  select(age_cat, Description_English) %>%
  tbl_summary(missing = "no",
              digits = list(all_categorical() ~ c(1,0)),
              type = list(all_continuous() ~ "continuous2"),
              statistic = list(all_continuous() ~ c("{mean} ({sd})",
                                                    "{min}, {max}")),
              by = age_cat,
              label = Description_English ~ ""
  ) %>%
  add_overall() %>%
  modify_header(label ~ "**Vegetables**") %>%
  bold_labels() %>%  
  as_flex_table() 

```

